---
title: "Supplement - AIC Tables - Pods Full"
date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
  compute: TRUE
output: 
  html_document:
    toc: true
---
<!-- Explore caching options (cache.path=mwCache, cache=params$compute) -->

# Initialization

```{r initialize, message=FALSE}
library(milkweed)
library(dplyr)
library(tidyr)
library(ggplot2)
library(lme4)
library(AICcmodavg)
library(vegan)
library(flextable)
library(webshot)

requirePackages("DHARMa")

data("stemdata")
metadata <- stemdata
metadata$year <- factor(metadata$year)
metadata$transect <- factor(metadata$transect)

# https://stat.ethz.ch/pipermail/r-sig-mixed-models/2014q4/022870.html
glmerCtrl <- glmerControl(optimizer = c("bobyqa"), optCtrl = list(maxfun=50000))
lmerCtrl <- lmerControl(optimizer = c("bobyqa"), optCtrl = list(maxfun=50000))

mwCache <- getOption("milkweed.cache")
```

```{r}
metadata_usc <- metadata %>% filter(!is.na(h_apical),
                                    !is.na(h_apical.next),
                                    !is.na(herb_avg),
                                    fec.flower == 1, #pods only result from the sexual pathway
                                    surv == 1, #again, plants must survive to September
                                    !is.na(N_pods),
                                    h_apical.next > 50,
                                    !(site == "YTB" & h_apical <= 50) #necessary to compensate for an issue with some of the plants in YTB site
                                    ) 

metadata_sc <- metadata_usc %>% mutate_at(.vars = vars(h_apical, h_apical.next, herb_avg),
                                          .funs = ~ as.numeric(scale(.)))

# Get scaling parameters (really just mean and sd)
h_apical_sc <- scale(metadata_usc$h_apical)
h_apical.next_sc <- scale(metadata_usc$h_apical.next)
herb_avg_sc <- scale(metadata_usc$herb_avg)
```

### June vs. September Height as a Predictor
First, do full model. In this case, we will compare to see if height in June or September is a better predictor.
```{r}
pods.reg.full_sept = glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next*herb_avg|site/transect)+(h_apical.next*herb_avg|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control=glmerCtrl)

pods.reg.full_june = glmer(N_pods ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect)+(h_apical*herb_avg|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control=glmerCtrl)

aictab(list(pods.reg.full_june, pods.reg.full_sept), modnames = c('June', 'September'))
summary(pods.reg.full_sept)
```

### Random Effects
September wins, so we will continue to use this in our model instead of height in June (h_apical). Now onto selection for random effects. We can try and drop the herb_avg term in the site/transect random effect first due to small variation.

Use nAGQ = 0 for quick approximations, but less exact form of parameter estimation.
```{r}
compute <- params$compute
savefile <- "aictabs_PF_RE_Site.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 3 terms
  pods.re.site_haThe.year_haThe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next*herb_avg|site/transect) + (h_apical.next*herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  # 2 terms
  pods.re.site_hePhaIhe.year_haThe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next:herb_avg + herb_avg|site/transect) + (h_apical.next*herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_haPhaIhe.year_haThe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next + h_apical.next:herb_avg|site/transect) + (h_apical.next*herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_haPhe.year_haThe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next + herb_avg|site/transect) + (h_apical.next*herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  # 1 term
  pods.re.site_he.year_haThe <- glmer(N_pods ~ h_apical.next*herb_avg + (herb_avg|site/transect) + (h_apical.next*herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_ha.year_haThe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next|site/transect) + (h_apical.next*herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_haIhe.year_haThe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next:herb_avg|site/transect) + (h_apical.next*herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  # 0 terms
  pods.re.site_1.year_haThe <- glmer(N_pods ~ h_apical.next*herb_avg + (1|site/transect) + (h_apical.next*herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  save(pods.re.site_haThe.year_haThe,
       pods.re.site_hePhaIhe.year_haThe,
       pods.re.site_haPhaIhe.year_haThe,
       pods.re.site_haPhe.year_haThe,
       pods.re.site_he.year_haThe,
       pods.re.site_ha.year_haThe,
       pods.re.site_haIhe.year_haThe,
       pods.re.site_1.year_haThe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r}
pods.re.site.AIC <- aictab(list(pods.re.site_haThe.year_haThe,
            pods.re.site_hePhaIhe.year_haThe,
            pods.re.site_haPhaIhe.year_haThe,
            pods.re.site_haPhe.year_haThe,
            pods.re.site_he.year_haThe,
            pods.re.site_ha.year_haThe,
            pods.re.site_haIhe.year_haThe,
            pods.re.site_1.year_haThe),
       modnames = c("Site: height*herb", 
                    "Site: herb + height:herb", 
                    "Site: height + height:herb", 
                    "Site: height + herb",
                    "Site: herb",
                    "Site: height",
                    "Site: height:herb",
                    "Site: 1"))
pods.re.site.AIC
```

Height on site wins.  Let's move on the year.
```{r}
compute <- params$compute
savefile <- "aictabs_PF_RE_Site_Year.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 2 terms
  pods.re.site_ha.year_haPhe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next|site/transect) + (h_apical.next+herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_ha.year_haPhaIhe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next|site/transect) + (h_apical.next+h_apical.next:herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_ha.year_hePhaIhe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next|site/transect) + (h_apical.next:herb_avg + herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  # 1 term
  pods.re.site_ha.year_he <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_ha.year_ha <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next|site/transect) + (h_apical.next|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_ha.year_haIhe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next|site/transect) + (h_apical.next:herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  # 0 terms
  pods.re.site_ha.year_1 <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next|site/transect) + (1|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  save(pods.re.site_ha.year_haThe,
       pods.re.site_ha.year_hePhaIhe,
       pods.re.site_ha.year_haPhaIhe,
       pods.re.site_ha.year_haPhe,
       pods.re.site_ha.year_he,
       pods.re.site_ha.year_ha,
       pods.re.site_ha.year_haIhe,
       pods.re.site_ha.year_1, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r}
p.re.year.AIC <- aictab(list(pods.re.site_ha.year_haThe,
            pods.re.site_ha.year_hePhaIhe,
            pods.re.site_ha.year_haPhaIhe,
            pods.re.site_ha.year_haPhe,
            pods.re.site_ha.year_he,
            pods.re.site_ha.year_ha,
            pods.re.site_ha.year_haIhe,
            pods.re.site_ha.year_1),
       modnames = c("Year: height*herb", 
                    "Year: herb + height:herb", 
                    "Year: height + height:herb", 
                    "Year: height + herb",
                    "Year: herb",
                    "Year: height",
                    "Year: height:herb",
                    "Year: 1"))

p.re.year.AIC
```
height + herbivory, and herbivory + height:herbivory are both year winners. Let's try starting from year.


```{r}
compute <- params$compute
savefile <- "aictabs_PF_RE_Year.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 2 terms
  pods.re.site_haThe.year_haPhe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next*herb_avg|site/transect) + (h_apical.next+herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_haThe.year_haPhaIhe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next*herb_avg|site/transect) + (h_apical.next+h_apical.next:herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_haThe.year_hePhaIhe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next*herb_avg|site/transect) + (h_apical.next:herb_avg + herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  # 1 term
  pods.re.site_haThe.year_he <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next*herb_avg|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_haThe.year_ha <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next*herb_avg|site/transect) + (h_apical.next|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_haThe.year_haIhe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next*herb_avg|site/transect) + (h_apical.next:herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  # 0 terms
  pods.re.site_haThe.year_1 <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next*herb_avg|site/transect) + (1|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  save(pods.re.site_haThe.year_haThe,
       pods.re.site_haThe.year_hePhaIhe,
       pods.re.site_haThe.year_haPhaIhe,
       pods.re.site_haThe.year_haPhe,
       pods.re.site_haThe.year_he,
       pods.re.site_haThe.year_ha,
       pods.re.site_haThe.year_haIhe,
       pods.re.site_haThe.year_1, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r}
p.re.year.AIC <- aictab(list(pods.re.site_haThe.year_haThe,
            pods.re.site_haThe.year_hePhaIhe,
            pods.re.site_haThe.year_haPhaIhe,
            pods.re.site_haThe.year_haPhe,
            pods.re.site_haThe.year_he,
            pods.re.site_haThe.year_ha,
            pods.re.site_haThe.year_haIhe,
            pods.re.site_haThe.year_1),
       modnames = c("Year: height*herb", 
                    "Year: herb + height:herb", 
                    "Year: height + height:herb", 
                    "Year: height + herb",
                    "Year: herb",
                    "Year: height",
                    "Year: height:herb",
                    "Year: 1"))

p.re.year.AIC
```

Winners:
Site: height, Year: herb
Site: height, year: height + herb

Now onto site, starting with random effect on year being just herbivory.

```{r}
compute <- params$compute
savefile <- "aictabs_PF_RE_Year_Site_1.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 3 terms
  pods.re.site_haThe.year_he <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next*herb_avg|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  # 2 terms
  pods.re.site_hePhaIhe.year_he <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next:herb_avg + herb_avg|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_haPhaIhe.year_he <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next + h_apical.next:herb_avg|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_haPhe.year_he <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next + herb_avg|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  # 1 term
  pods.re.site_he.year_he <- glmer(N_pods ~ h_apical.next*herb_avg + (herb_avg|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_ha.year_he <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_haIhe.year_he <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next:herb_avg|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  # 0 terms
  pods.re.site_1.year_he <- glmer(N_pods ~ h_apical.next*herb_avg + (1|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  save(pods.re.site_haThe.year_he,
       pods.re.site_hePhaIhe.year_he,
       pods.re.site_haPhaIhe.year_he,
       pods.re.site_haPhe.year_he,
       pods.re.site_he.year_he,
       pods.re.site_ha.year_he,
       pods.re.site_haIhe.year_he,
       pods.re.site_1.year_he, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

Now with year: height + herbivory

```{r}
compute <- params$compute
savefile <- "aictabs_PF_RE_Year_Site_2.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 3 terms
  pods.re.site_haThe.year_haPhe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next*herb_avg|site/transect) + (h_apical.next + herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  # 2 terms
  pods.re.site_hePhaIhe.year_haPhe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next:herb_avg + herb_avg|site/transect) + (h_apical.next + herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_haPhaIhe.year_haPhe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next + h_apical.next:herb_avg|site/transect) + (h_apical.next + herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_haPhe.year_haPhe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next + herb_avg|site/transect) + (h_apical.next + herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  # 1 term
  pods.re.site_he.year_haPhe <- glmer(N_pods ~ h_apical.next*herb_avg + (herb_avg|site/transect) + (h_apical.next + herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_ha.year_haPhe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next|site/transect) + (h_apical.next + herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_haIhe.year_haPhe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next:herb_avg|site/transect) + (h_apical.next + herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  # 0 terms
  pods.re.site_1.year_haPhe <- glmer(N_pods ~ h_apical.next*herb_avg + (1|site/transect) + (h_apical.next + herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  save(pods.re.site_haThe.year_haPhe,
       pods.re.site_hePhaIhe.year_haPhe,
       pods.re.site_haPhaIhe.year_haPhe,
       pods.re.site_haPhe.year_haPhe,
       pods.re.site_he.year_haPhe,
       pods.re.site_ha.year_haPhe,
       pods.re.site_haIhe.year_haPhe,
       pods.re.site_1.year_haPhe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r}
aictab(list(pods.re.site_haThe.year_haPhe,
       pods.re.site_hePhaIhe.year_haPhe,
       pods.re.site_haPhaIhe.year_haPhe,
       pods.re.site_haPhe.year_haPhe,
       pods.re.site_he.year_haPhe,
       pods.re.site_ha.year_haPhe,
       pods.re.site_haIhe.year_haPhe,
       pods.re.site_1.year_haPhe,
       pods.re.site_haThe.year_he,
       pods.re.site_hePhaIhe.year_he,
       pods.re.site_haPhaIhe.year_he,
       pods.re.site_haPhe.year_he,
       pods.re.site_he.year_he,
       pods.re.site_ha.year_he,
       pods.re.site_haIhe.year_he,
       pods.re.site_1.year_he),
       modnames = c("Site: height*herb, Year: height + herb", 
                    "Site: herb + height:herb, Year: height + herb", 
                    "Site: height + height:herb, Year: height + herb", 
                    "Site: height + herb, Year: height + herb",
                    "Site: herb, Year: height + herb",
                    "Site: height, Year: height + herb",
                    "Site: height:herb, Year: height + herb",
                    "Site: 1, Year: height + herb",
                    "Site: height*herb, Year: herb", 
                    "Site: herb + height:herb, Year: herb", 
                    "Site: height + height:herb, Year: herb", 
                    "Site: height + herb, Year: herb",
                    "Site: herb, Year: herb",
                    "Site: height, Year: herb",
                    "Site: height:herb, Year: herb",
                    "Site: 1, Year: herb"))
```
Winners:
Site: height, Year: height+herb
Site: height+height:herb, Year: height+herb
Site: height+herb, Year: height+herb
Site: height+height:herb, Year: herb

AIC of all winners

```{r}
aictab(list(pods.re.site_ha.year_haPhe,
            pods.re.site_ha.year_he,
            pods.re.site_haPhaIhe.year_haPhe,
            pods.re.site_haPhe.year_haPhe,
            pods.re.site_haPhaIhe.year_he),
       modnames = c("Site: height, Year: height + herb",
                    "Site: height, Year: herb",
                    "Site: height+height:herb, Year: height+herb",
                    "Site: height+herb, Year: height+herb",
                    "Site: height+height:herb, Year: herb"))
```
Winners:
Site: height, year: height+herb
Site: height+height:herb, year: height+herb,
Site: height+herb, year: height+herb
Site: height+height:herb, year:herb

Note that the final three winners only emerged when starting with year.

## Singularity

Let's start with our most complex model, site: height+herb and year: height+herb

```{r}
compute <- params$compute
savefile <- "aictabs_PF_Sing_1.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
    pods.re.site_haPhe.year_haPhe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next+herb_avg|site/transect) + (h_apical.next + herb_avg|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control = glmerCtrl)

  save(pods.re.site_haPhe.year_haPhe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
rePCA(pods.re.site_haPhe.year_haPhe)
```

Let's drop herbivory on site, giving us one of our other winning models.

```{r}
compute <- params$compute
savefile <- "aictabs_PF_Sing_2.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
    pods.re.site_ha.year_haPhe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next|site/transect) + (h_apical.next + herb_avg|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control = glmerCtrl)

  save(pods.re.site_ha.year_haPhe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
rePCA(pods.re.site_ha.year_haPhe)
```
Still singular. Drop height on site. 

```{r}
compute <- params$compute
savefile <- "aictabs_PF_Sing_3.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
    pods.re.site_1.year_haPhe <- glmer(N_pods ~ h_apical.next*herb_avg + (1|site/transect) + (h_apical.next + herb_avg|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control = glmerCtrl)

  save(pods.re.site_1.year_haPhe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
rePCA(pods.re.site_1.year_haPhe)
```
Nonsingular model achieved!

Let's go back to the beginning and try Site: height+height:herb, Year: height+herb

```{r}
compute <- params$compute
savefile <- "aictabs_PF_Sing_4.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
    pods.re.site_haPhaIhe.year_haPhe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next+h_apical.next:herb_avg|site/transect) + (h_apical.next + herb_avg|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control = glmerCtrl)

  save(pods.re.site_haPhaIhe.year_haPhe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
rePCA(pods.re.site_haPhaIhe.year_haPhe)
```
Still singular. Dropping the interaction term on site would give us the model we went through earlier.

Let's go back to the beginning and try Site: height+height:herb, year: herb

```{r}
compute <- params$compute
savefile <- "aictabs_PF_Sing_5.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
    pods.re.site_haPhaIhe.year_he <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next+h_apical.next:herb_avg|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control = glmerCtrl)

  save(pods.re.site_haPhaIhe.year_he, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
rePCA(pods.re.site_haPhaIhe.year_he)
```
Drop interaction term on site.

```{r}
compute <- params$compute
savefile <- "aictabs_PF_Sing_6.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
    pods.re.site_ha.year_he <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control = glmerCtrl)

  save(pods.re.site_ha.year_he, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
rePCA(pods.re.site_ha.year_he)
```
Nonsingular model!

Nonsingular AIC

```{r}
aictab(list(pods.re.site_1.year_haPhe,
            pods.re.site_ha.year_he),
       modnames = c("Site: 1, Year: height+herb",
                    "Site: height, Year: herb"))
```

Winner is site: height, year: herb


# Fixed Effects

```{r}
compute <- params$compute
savefile <- "aictabs_PF_FE.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 3 terms
  pods.fe.haThe.re.site_ha.year_he <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control=glmerCtrl)
  
  # 2 terms
  pods.fe.haPhe.re.site_ha.year_he <- glmer(N_pods ~ h_apical.next+herb_avg + (h_apical.next|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control=glmerCtrl)
  
  pods.fe.haPhaIhe.re.site_ha.year_he <- glmer(N_pods ~ h_apical.next+h_apical.next:herb_avg + (h_apical.next|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control=glmerCtrl)
  
  pods.fe.hePhaIhe.re.site_ha.year_he <- glmer(N_pods ~ h_apical.next:herb_avg + herb_avg + (h_apical.next|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control=glmerCtrl)
  
  # 1 term
  pods.fe.ha.re.site_ha.year_he <- glmer(N_pods ~ h_apical.next + (h_apical.next|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control=glmerCtrl)
  
  pods.fe.he.re.site_ha.year_he <- glmer(N_pods ~ herb_avg + (h_apical.next|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control=glmerCtrl)
  
  pods.fe.haIhe.re.site_ha.year_he <- glmer(N_pods ~ h_apical.next:herb_avg + (h_apical.next|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control=glmerCtrl)
  
  # 0 terms
  pods.fe.1.re.site_ha.year_he <- glmer(N_pods ~ 1 + (h_apical.next|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control=glmerCtrl)
  
  save(pods.fe.haThe.re.site_ha.year_he,
       pods.fe.hePhaIhe.re.site_ha.year_he,
       pods.fe.haPhaIhe.re.site_ha.year_he,
       pods.fe.haPhe.re.site_ha.year_he,
       pods.fe.he.re.site_ha.year_he,
       pods.fe.ha.re.site_ha.year_he,
       pods.fe.haIhe.re.site_ha.year_he,
       pods.fe.1.re.site_ha.year_he, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r}
p.fe.AIC <- aictab(list(pods.fe.haThe.re.site_ha.year_he,
       pods.fe.hePhaIhe.re.site_ha.year_he,
       pods.fe.haPhaIhe.re.site_ha.year_he,
       pods.fe.haPhe.re.site_ha.year_he,
       pods.fe.he.re.site_ha.year_he,
       pods.fe.ha.re.site_ha.year_he,
       pods.fe.haIhe.re.site_ha.year_he,
       pods.fe.1.re.site_ha.year_he),
       modnames = c("Fixed: height*herb", 
                    "Fixed: herb + height:herb", 
                    "Fixed: height + height:herb", 
                    "Fixed: height + herb",
                    "Fixed: herb",
                    "Fixed: height",
                    "Fixed: height:herb",
                    "Fixed: 1"))
p.fe.AIC
```

height+height:herbivory is the most complex model with 3 AIC, so let's take that as our winning model.

Winner:
```{r}
summary(pods.fe.haPhaIhe.re.site_ha.year_he)
```

# Model Validation and Diagnostics
```{r}
par(mfrow=c(2,2))
plot(fitted(pods.fe.haPhaIhe.re.site_ha.year_he), residuals(pods.fe.haPhaIhe.re.site_ha.year_he, "deviance"), xlab="Fitted values", ylab="Deviance residuals")
plot(metadata_sc$h_apical, residuals(pods.fe.haPhaIhe.re.site_ha.year_he, "deviance"), xlab="Apical height", ylab="Deviance residuals")
plot(metadata_sc$herb_avg, residuals(pods.fe.haPhaIhe.re.site_ha.year_he, "deviance"), xlab="Herbivory average", ylab="Deviance residuals")
par(mfrow=c(1,1))
```

DHARMa Diagnostics
```{r}
pods.simulationOutput = DHARMa::simulateResiduals(fittedModel = pods.fe.haPhaIhe.re.site_ha.year_he, n=1000)
```


```{r}
DHARMa::plotSimulatedResiduals(pods.simulationOutput)
DHARMa::plotResiduals(metadata_sc$h_apical, pods.simulationOutput$scaledResiduals)
DHARMa::plotResiduals(metadata_sc$herb_avg, pods.simulationOutput$scaledResiduals)
```

Data looks good with some serious deviation at the upper end.

```{r}
DHARMa::testUniformity(pods.simulationOutput)
```


