---
title: "Supplement - AIC Tables - Survival"
date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
  compute: TRUE
output: 
  html_document:
    toc: true
---
<!-- Explore caching options (cache.path=mwCache, cache=params$compute) -->

# Initialization

```{r initialize, message=FALSE}
library(milkweed)
library(dplyr)
library(tidyr)
library(ggplot2)
library(lme4)
library(AICcmodavg)
library(vegan)
library(flextable)
library(webshot)

requirePackages("DHARMa")

data("stemdata")
metadata <- stemdata
metadata$year <- factor(metadata$year)
metadata$transect <- factor(metadata$transect)

# https://stat.ethz.ch/pipermail/r-sig-mixed-models/2014q4/022870.html
glmerCtrl <- glmerControl(optimizer = c("bobyqa"), optCtrl = list(maxfun=50000))
lmerCtrl <- lmerControl(optimizer = c("bobyqa"), optCtrl = list(maxfun=50000))

mwCache <- getOption("milkweed.cache")
```

```{r flowering scaling}
metadata_usc <- metadata %>% filter(!is.na(h_apical),
                                    !is.na(herb_avg),
                                    !is.na(surv),
                                    fec.flower == 1,
                                    !(year %in% c('2017')),
                                    !(site %in% c('GET', 'GRN'))
                                    )

metadata_sc <- metadata_usc %>% mutate_at(.vars = vars(h_apical, herb_avg),
                                          .funs = ~ as.numeric(scale(.))) 

# Get scaling parameters (really just mean and sd)
h_apical_sc <- scale(metadata_usc$h_apical)
herb_avg_sc <- scale(metadata_usc$herb_avg)
```

## Random Effects

Use nAGQ = 0 for quick approximations, but less exact form of parameter estimation.
```{r}
compute <- params$compute
savefile <- "aictabs_S_RE_Site.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 3 terms
  surv.re.site_haThe.year_haThe <- glmer(surv ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 2 terms
  surv.re.site_hePhaIhe.year_haThe <- glmer(surv ~ h_apical*herb_avg + (h_apical:herb_avg + herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_haPhaIhe.year_haThe <- glmer(surv ~ h_apical*herb_avg + (h_apical + h_apical:herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_haPhe.year_haThe <- glmer(surv ~ h_apical*herb_avg + (h_apical + herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 1 term
  surv.re.site_he.year_haThe <- glmer(surv ~ h_apical*herb_avg + (herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_ha.year_haThe <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_haIhe.year_haThe <- glmer(surv ~ h_apical*herb_avg + (h_apical:herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 0 terms
  surv.re.site_1.year_haThe <- glmer(surv ~ h_apical*herb_avg + (1|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  save(surv.re.site_haThe.year_haThe,
       surv.re.site_hePhaIhe.year_haThe,
       surv.re.site_haPhaIhe.year_haThe,
       surv.re.site_haPhe.year_haThe,
       surv.re.site_he.year_haThe,
       surv.re.site_ha.year_haThe,
       surv.re.site_haIhe.year_haThe,
       surv.re.site_1.year_haThe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r}
s.re.site.AIC <- aictab(list(surv.re.site_haThe.year_haThe,
            surv.re.site_hePhaIhe.year_haThe,
            surv.re.site_haPhaIhe.year_haThe,
            surv.re.site_haPhe.year_haThe,
            surv.re.site_he.year_haThe,
            surv.re.site_ha.year_haThe,
            surv.re.site_haIhe.year_haThe,
            surv.re.site_1.year_haThe),
       modnames = c("Site: height*herb", 
                    "Site: herb + height:herb", 
                    "Site: height + height:herb", 
                    "Site: height + herb",
                    "Site: herb",
                    "Site: height",
                    "Site: height:herb",
                    "Site: 1"))
s.re.site.AIC
```

Height, herbivory, and no parameter are all winners, so we will proceed with all three in that order.

```{r}
compute <- params$compute
savefile <- "aictabs_S_RE_Site_Year_1.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 2 terms
  surv.re.site_ha.year_haPhe <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_ha.year_haPhaIhe <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_ha.year_hePhaIhe <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical:herb_avg + herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 1 term
  surv.re.site_ha.year_he <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_ha.year_ha <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_ha.year_haIhe <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 0 terms
  surv.re.site_ha.year_1 <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (1|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  save(surv.re.site_ha.year_haThe,
       surv.re.site_ha.year_hePhaIhe,
       surv.re.site_ha.year_haPhaIhe,
       surv.re.site_ha.year_haPhe,
       surv.re.site_ha.year_he,
       surv.re.site_ha.year_ha,
       surv.re.site_ha.year_haIhe,
       surv.re.site_ha.year_1, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

Now herbivory

```{r}
compute <- params$compute
savefile <- "aictabs_S_RE_Site_Year_2.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 2 terms
  surv.re.site_he.year_haPhe <- glmer(surv ~ h_apical*herb_avg + (herb_avg|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_he.year_haPhaIhe <- glmer(surv ~ h_apical*herb_avg + (herb_avg|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_he.year_hePhaIhe <- glmer(surv ~ h_apical*herb_avg + (herb_avg|site/transect) + (h_apical:herb_avg + herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 1 term
  surv.re.site_he.year_he <- glmer(surv ~ h_apical*herb_avg + (herb_avg|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_he.year_ha <- glmer(surv ~ h_apical*herb_avg + (herb_avg|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_he.year_haIhe <- glmer(surv ~ h_apical*herb_avg + (herb_avg|site/transect) + (h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 0 terms
  surv.re.site_he.year_1 <- glmer(surv ~ h_apical*herb_avg + (herb_avg|site/transect) + (1|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  save(surv.re.site_he.year_haThe,
       surv.re.site_he.year_hePhaIhe,
       surv.re.site_he.year_haPhaIhe,
       surv.re.site_he.year_haPhe,
       surv.re.site_he.year_he,
       surv.re.site_he.year_ha,
       surv.re.site_he.year_haIhe,
       surv.re.site_he.year_1, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

Now intercept

```{r}
compute <- params$compute
savefile <- "aictabs_S_RE_Site_Year_3.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 2 terms
  surv.re.site_1.year_haPhe <- glmer(surv ~ h_apical*herb_avg + (1|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_1.year_haPhaIhe <- glmer(surv ~ h_apical*herb_avg + (1|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_1.year_hePhaIhe <- glmer(surv ~ h_apical*herb_avg + (1|site/transect) + (h_apical:herb_avg + herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 1 term
  surv.re.site_1.year_he <- glmer(surv ~ h_apical*herb_avg + (1|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_1.year_ha <- glmer(surv ~ h_apical*herb_avg + (1|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_1.year_haIhe <- glmer(surv ~ h_apical*herb_avg + (1|site/transect) + (h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 0 terms
  surv.re.site_1.year_1 <- glmer(surv ~ h_apical*herb_avg + (1|site/transect) + (1|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  save(surv.re.site_1.year_haThe,
       surv.re.site_1.year_hePhaIhe,
       surv.re.site_1.year_haPhaIhe,
       surv.re.site_1.year_haPhe,
       surv.re.site_1.year_he,
       surv.re.site_1.year_ha,
       surv.re.site_1.year_haIhe,
       surv.re.site_1.year_1, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r}
aictab(list(surv.re.site_ha.year_haThe,
       surv.re.site_ha.year_hePhaIhe,
       surv.re.site_ha.year_haPhaIhe,
       surv.re.site_ha.year_haPhe,
       surv.re.site_ha.year_he,
       surv.re.site_ha.year_ha,
       surv.re.site_ha.year_haIhe,
       surv.re.site_ha.year_1,
       surv.re.site_he.year_haThe,
       surv.re.site_he.year_hePhaIhe,
       surv.re.site_he.year_haPhaIhe,
       surv.re.site_he.year_haPhe,
       surv.re.site_he.year_he,
       surv.re.site_he.year_ha,
       surv.re.site_he.year_haIhe,
       surv.re.site_he.year_1,
       surv.re.site_1.year_haThe,
       surv.re.site_1.year_hePhaIhe,
       surv.re.site_1.year_haPhaIhe,
       surv.re.site_1.year_haPhe,
       surv.re.site_1.year_he,
       surv.re.site_1.year_ha,
       surv.re.site_1.year_haIhe,
       surv.re.site_1.year_1),
       modnames = c("Site: height, Year: height*herb", 
                    "Site: height, Year: herb + height:herb", 
                    "Site: height, Year: height + height:herb", 
                    "Site: height, Year: height + herb",
                    "Site: height, Year: herb",
                    "Site: height, Year: height",
                    "Site: height, Year: height:herb",
                    "Site: height, Year: 1",
                    "Site: herbivory, Year: height*herb", 
                    "Site: herbivory, Year: herb + height:herb", 
                    "Site: herbivory, Year: height + height:herb", 
                    "Site: herbivory, Year: height + herb",
                    "Site: herbivory, Year: herb",
                    "Site: herbivory, Year: height",
                    "Site: herbivory, Year: height:herb",
                    "Site: herbivory, Year: 1",
                    "Site: 1, Year: height*herb", 
                    "Site: 1, Year: herb + height:herb", 
                    "Site: 1, Year: height + height:herb", 
                    "Site: 1, Year: height + herb",
                    "Site: 1, Year: herb",
                    "Site: 1, Year: height",
                    "Site: 1, Year: height:herb",
                    "Site: 1, Year: 1"))
```
Winners: 
Site: height, Year: height + herb
Site: herbivory, Year: height
Site: herbivory, Year: height + herb
Site: 1, Year: height + herb

## Starting with year

```{r}
compute <- params$compute
savefile <- "aictabs_S_RE_Year.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  
  #3 terms
  surv.re.site_haThe.year_haThe <- glmer(surv ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 2 terms
  surv.re.site_haThe.year_haPhe <- glmer(surv ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_haThe.year_haPhaIhe <- glmer(surv ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_haThe.year_hePhaIhe <- glmer(surv ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical:herb_avg + herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 1 term
  surv.re.site_haThe.year_he <- glmer(surv ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_haThe.year_ha <- glmer(surv ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_haThe.year_haIhe <- glmer(surv ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 0 terms
  surv.re.site_haThe.year_1 <- glmer(surv ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (1|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  save(surv.re.site_haThe.year_haThe,
       surv.re.site_haThe.year_hePhaIhe,
       surv.re.site_haThe.year_haPhaIhe,
       surv.re.site_haThe.year_haPhe,
       surv.re.site_haThe.year_he,
       surv.re.site_haThe.year_ha,
       surv.re.site_haThe.year_haIhe,
       surv.re.site_haThe.year_1, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r}
aictab(list(surv.re.site_haThe.year_haThe,
       surv.re.site_haThe.year_hePhaIhe,
       surv.re.site_haThe.year_haPhaIhe,
       surv.re.site_haThe.year_haPhe,
       surv.re.site_haThe.year_he,
       surv.re.site_haThe.year_ha,
       surv.re.site_haThe.year_haIhe,
       surv.re.site_haThe.year_1),
       modnames = c("Year: height*herb", 
                    "Year: herb + height:herb", 
                    "Year: height + height:herb", 
                    "Year: height + herb",
                    "Year: herb",
                    "Year: height",
                    "Year: height:herb",
                    "Year: 1"))
```
Year winners:
height + herb, height, and height + height:herb

Starting with height

```{r}
compute <- params$compute
savefile <- "aictabs_S_RE_Year_Site_1.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 3 terms
  surv.re.site_haThe.year_ha <- glmer(surv ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 2 terms
  surv.re.site_hePhaIhe.year_ha <- glmer(surv ~ h_apical*herb_avg + (h_apical:herb_avg + herb_avg|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_haPhaIhe.year_ha <- glmer(surv ~ h_apical*herb_avg + (h_apical + h_apical:herb_avg|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_haPhe.year_ha <- glmer(surv ~ h_apical*herb_avg + (h_apical + herb_avg|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 1 term
  surv.re.site_he.year_ha <- glmer(surv ~ h_apical*herb_avg + (herb_avg|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_ha.year_ha <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_haIhe.year_ha <- glmer(surv ~ h_apical*herb_avg + (h_apical:herb_avg|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 0 terms
  surv.re.site_1.year_ha <- glmer(surv ~ h_apical*herb_avg + (1|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  save(surv.re.site_haThe.year_ha,
       surv.re.site_hePhaIhe.year_ha,
       surv.re.site_haPhaIhe.year_ha,
       surv.re.site_haPhe.year_ha,
       surv.re.site_he.year_ha,
       surv.re.site_ha.year_ha,
       surv.re.site_haIhe.year_ha,
       surv.re.site_1.year_ha, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

Now height + herbivory

```{r}
compute <- params$compute
savefile <- "aictabs_S_RE_Year_Site_2.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 3 terms
  surv.re.site_haThe.year_haPhe <- glmer(surv ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 2 terms
  surv.re.site_hePhaIhe.year_haPhe <- glmer(surv ~ h_apical*herb_avg + (h_apical:herb_avg + herb_avg|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_haPhaIhe.year_haPhe <- glmer(surv ~ h_apical*herb_avg + (h_apical + h_apical:herb_avg|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_haPhe.year_haPhe <- glmer(surv ~ h_apical*herb_avg + (h_apical + herb_avg|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 1 term
  surv.re.site_he.year_haPhe <- glmer(surv ~ h_apical*herb_avg + (herb_avg|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_ha.year_haPhe <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_haIhe.year_haPhe <- glmer(surv ~ h_apical*herb_avg + (h_apical:herb_avg|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 0 terms
  surv.re.site_1.year_haPhe <- glmer(surv ~ h_apical*herb_avg + (1|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  save(surv.re.site_haThe.year_haPhe,
       surv.re.site_hePhaIhe.year_haPhe,
       surv.re.site_haPhaIhe.year_haPhe,
       surv.re.site_haPhe.year_haPhe,
       surv.re.site_he.year_haPhe,
       surv.re.site_ha.year_haPhe,
       surv.re.site_haIhe.year_haPhe,
       surv.re.site_1.year_haPhe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

Now height + height:herbivory

```{r}
compute <- params$compute
savefile <- "aictabs_S_RE_Year_Site_3.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 3 terms
  surv.re.site_haThe.year_haPhaIhe <- glmer(surv ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 2 terms
  surv.re.site_hePhaIhe.year_haPhaIhe <- glmer(surv ~ h_apical*herb_avg + (h_apical:herb_avg + herb_avg|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_haPhaIhe.year_haPhaIhe <- glmer(surv ~ h_apical*herb_avg + (h_apical + h_apical:herb_avg|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_haPhe.year_haPhaIhe <- glmer(surv ~ h_apical*herb_avg + (h_apical + herb_avg|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 1 term
  surv.re.site_he.year_haPhaIhe <- glmer(surv ~ h_apical*herb_avg + (herb_avg|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_ha.year_haPhaIhe <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_haIhe.year_haPhaIhe <- glmer(surv ~ h_apical*herb_avg + (h_apical:herb_avg|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 0 terms
  surv.re.site_1.year_haPhaIhe <- glmer(surv ~ h_apical*herb_avg + (1|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  save(surv.re.site_haThe.year_haPhaIhe,
       surv.re.site_hePhaIhe.year_haPhaIhe,
       surv.re.site_haPhaIhe.year_haPhaIhe,
       surv.re.site_haPhe.year_haPhaIhe,
       surv.re.site_he.year_haPhaIhe,
       surv.re.site_ha.year_haPhaIhe,
       surv.re.site_haIhe.year_haPhaIhe,
       surv.re.site_1.year_haPhaIhe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r}
aictab(list(surv.re.site_haThe.year_ha,
       surv.re.site_hePhaIhe.year_ha,
       surv.re.site_haPhaIhe.year_ha,
       surv.re.site_haPhe.year_ha,
       surv.re.site_he.year_ha,
       surv.re.site_ha.year_ha,
       surv.re.site_haIhe.year_ha,
       surv.re.site_1.year_ha,
       surv.re.site_haThe.year_haPhe,
       surv.re.site_hePhaIhe.year_haPhe,
       surv.re.site_haPhaIhe.year_haPhe,
       surv.re.site_haPhe.year_haPhe,
       surv.re.site_he.year_haPhe,
       surv.re.site_ha.year_haPhe,
       surv.re.site_haIhe.year_haPhe,
       surv.re.site_1.year_haPhe,
       surv.re.site_haThe.year_haPhaIhe,
       surv.re.site_hePhaIhe.year_haPhaIhe,
       surv.re.site_haPhaIhe.year_haPhaIhe,
       surv.re.site_haPhe.year_haPhaIhe,
       surv.re.site_he.year_haPhaIhe,
       surv.re.site_ha.year_haPhaIhe,
       surv.re.site_haIhe.year_haPhaIhe,
       surv.re.site_1.year_haPhaIhe),
       modnames = c("Site: height*herb, Year: height", 
                    "Site: herb + height:herb, Year: height", 
                    "Site: height + height:herb, Year: height", 
                    "Site: height + herb, Year: height",
                    "Site: herb, Year: height",
                    "Site: height, Year: height",
                    "Site: height:herb, Year: height",
                    "Site: 1, Year: height",
                    "Site: height*herb, Year: height + herb", 
                    "Site: herb + height:herb, Year: height + herb", 
                    "Site: height + height:herb, Year: height + herb", 
                    "Site: height + herb, Year: height + herb",
                    "Site: herb, Year: height + herb",
                    "Site: height, Year: height + herb",
                    "Site: height:herb, Year: height + herb",
                    "Site: 1, Year: height + herb",
                   "Site: height*herb, Year: height + height:herb", 
                    "Site: herb + height:herb, Year: height + height:herb", 
                    "Site: height + height:herb, Year: height + height:herb", 
                    "Site: height + herb, Year: height + height:herb",
                    "Site: herb, Year: height + height:herb",
                    "Site: height, Year: height + height:herb",
                    "Site: height:herb, Year: height + height:herb",
                   "Site: 1, Year: height + height:herb"))
```
This keeps the other 4 winners but adds Site: height+herb and Year: height+herb.

## Singularity

Let's start with the most complex model.

```{r}
compute <- params$compute
savefile <- "aictabs_S_Sing_1.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  surv.fe.haThe.re.site_haPhe.year_haPhe <- glmer(surv ~ h_apical*herb_avg + (h_apical+herb_avg|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)

  save(surv.fe.haThe.re.site_haPhe.year_haPhe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
rePCA(surv.fe.haThe.re.site_haPhe.year_haPhe)
```

Branch point 1. Try dropping height on site

```{r}
compute <- params$compute
savefile <- "aictabs_S_Sing_2.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  surv.fe.haThe.re.site_he.year_haPhe <- glmer(surv ~ h_apical*herb_avg + (herb_avg|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)

  save(surv.fe.haThe.re.site_he.year_haPhe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
rePCA(surv.fe.haThe.re.site_he.year_haPhe)
```
Now drop herbivory on site

```{r}
compute <- params$compute
savefile <- "aictabs_S_Sing_3.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  surv.fe.haThe.re.site_1.year_haPhe <- glmer(surv ~ h_apical*herb_avg + (1|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)

  save(surv.fe.haThe.re.site_1.year_haPhe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
rePCA(surv.fe.haThe.re.site_he.year_haPhe)
```
Non singular model: Site: 1, Year: height + herbivory

Return to branch point 1. Try keeping height and dropping herbivory instead

```{r}
compute <- params$compute
savefile <- "aictabs_S_Sing_3.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  surv.fe.haThe.re.site_ha.year_haPhe <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)

  save(surv.fe.haThe.re.site_ha.year_haPhe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
rePCA(surv.fe.haThe.re.site_ha.year_haPhe)
```

Try dropping herbivory on year

```{r}
compute <- params$compute
savefile <- "aictabs_S_Sing_4.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  surv.fe.haThe.re.site_ha.year_ha <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)

  save(surv.fe.haThe.re.site_ha.year_ha, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
rePCA(surv.fe.haThe.re.site_ha.year_ha)
```
Non-singular model achieved, but what if we dropped height instead?

```{r}
compute <- params$compute
savefile <- "aictabs_S_Sing_5.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  surv.fe.haThe.re.site_ha.year_he <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)

  save(surv.fe.haThe.re.site_ha.year_he, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
rePCA(surv.fe.haThe.re.site_ha.year_he)
```

Similarity in transect within site. Try removing the parameter on site.

```{r}
compute <- params$compute
savefile <- "aictabs_S_Sing_6.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  surv.fe.haThe.re.site_1.year_he <- glmer(surv ~ h_apical*herb_avg + (1|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)

  save(surv.fe.haThe.re.site_1.year_he, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
rePCA(surv.fe.haThe.re.site_1.year_he)
```

Another nonsingular model.

By dropping parameters from the most complex model, we iterated through all other winning models except for Site: herbivory, year: height. Let's try that one now.

```{r}
compute <- params$compute
savefile <- "aictabs_S_Sing_7.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  surv.fe.haThe.re.site_he.year_ha <- glmer(surv ~ h_apical*herb_avg + (herb_avg|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)

  save(surv.fe.haThe.re.site_he.year_ha, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
rePCA(surv.fe.haThe.re.site_he.year_ha)
```

Site is singular, dropping the variable in site gives an already determined model. Here are the nonsingular models we have generated:

Site: 1, Year: height+herb
Site: height, year: height
Site: 1, year: herb

Let's run an AIC analysis to see which of these models is best.

```{r}
aictab(list(surv.fe.haThe.re.site_1.year_haPhe,
            surv.fe.haThe.re.site_1.year_he,
            surv.fe.haThe.re.site_ha.year_ha),
       modnames = c("Site: 1, Year: height + herb",
                    "Site: 1, Year: herb",
                    "Site: height, Year: height"))
```
Winner is: 

Site: 1, Year: height + herbivory.

## Fixed Effects

```{r}
compute <- params$compute
savefile <- "aictabs_S_FE.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 2 terms
  surv.fe.haPhe.re.site_1.year_haPhe <- glmer(surv ~ h_apical+herb_avg + (1|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  surv.fe.haPhaIhe.re.site_1.year_haPhe <- glmer(surv ~ h_apical+h_apical:herb_avg + (1|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  surv.fe.hePhaIhe.re.site_1.year_haPhe <- glmer(surv ~ h_apical:herb_avg + herb_avg + (1|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  # 1 term
  surv.fe.ha.re.site_1.year_haPhe <- glmer(surv ~ h_apical + (1|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  surv.fe.he.re.site_1.year_haPhe <- glmer(surv ~ herb_avg + (1|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  surv.fe.haIhe.re.site_1.year_haPhe <- glmer(surv ~ h_apical:herb_avg + (1|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  # 0 terms
  surv.fe.1.re.site_1.year_haPhe <- glmer(surv ~ 1 + (1|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  save(surv.fe.haThe.re.site_1.year_haPhe,
       surv.fe.hePhaIhe.re.site_1.year_haPhe,
       surv.fe.haPhaIhe.re.site_1.year_haPhe,
       surv.fe.haPhe.re.site_1.year_haPhe,
       surv.fe.he.re.site_1.year_haPhe,
       surv.fe.ha.re.site_1.year_haPhe,
       surv.fe.haIhe.re.site_1.year_haPhe,
       surv.fe.1.re.site_1.year_haPhe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r}
s.fe.AIC <- aictab(list(surv.fe.haThe.re.site_1.year_haPhe,
       surv.fe.hePhaIhe.re.site_1.year_haPhe,
       surv.fe.haPhaIhe.re.site_1.year_haPhe,
       surv.fe.haPhe.re.site_1.year_haPhe,
       surv.fe.he.re.site_1.year_haPhe,
       surv.fe.ha.re.site_1.year_haPhe,
       surv.fe.haIhe.re.site_1.year_haPhe,
       surv.fe.1.re.site_1.year_haPhe),
       modnames = c("Fixed: height*herb", 
                    "Fixed: herb + height:herb", 
                    "Fixed: height + height:herb", 
                    "Fixed: height + herb",
                    "Fixed: herb",
                    "Fixed: height",
                    "Fixed: height:herb",
                    "Fixed: 1"))

s.fe.AIC
```
The intercept, herb, height, height:herb, herb + height:herb, and height + herb all fall within an AIC of 3, so let's choose the most complex model.


Winner:
```{r}
summary(surv.fe.haPhe.re.site_1.year_haPhe)
```

Now some diagnostics (aka model validation). Creating standard residual plots.
```{r}
par(mfrow=c(2,2))
plot(fitted(surv.fe.haPhe.re.site_1.year_haPhe), residuals(surv.fe.haPhe.re.site_1.year_haPhe, "deviance"), xlab="Fitted values", ylab="Deviance residuals")
plot(metadata_sc$h_apical, residuals(surv.fe.haPhe.re.site_1.year_haPhe, "deviance"), xlab="Apical height", ylab="Deviance residuals")
plot(metadata_sc$herb_avg, residuals(surv.fe.haPhe.re.site_1.year_haPhe, "deviance"), xlab="Herbivory average", ylab="Deviance residuals")
par(mfrow=c(1,1))
```

DHARMa Diagnostics. Same process as above. 
```{r}
surv.simulationOutput = DHARMa::simulateResiduals(fittedModel = surv.fe.haPhe.re.site_1.year_haPhe, n=1000)
```

```{r}
DHARMa::plotSimulatedResiduals(surv.simulationOutput)
DHARMa::plotResiduals(metadata_sc$h_apical, surv.simulationOutput$scaledResiduals)
DHARMa::plotResiduals(metadata_sc$herb_avg, surv.simulationOutput$scaledResiduals)
```
Plots look pretty good, some deviation in the QQ plot but not too much.

```{r}
DHARMa::testUniformity(surv.simulationOutput)
```
Do not pass uniformity test, though see notes in flowering about large sample size.

