---
title: "Supplement - AIC Tables - Growth"
date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
  compute: TRUE
output: 
  html_document:
    toc: true
---
<!-- Explore caching options (cache.path=mwCache, cache=params$compute) -->

# Initialization

```{r initialize, message=FALSE}
library(milkweed)
library(dplyr)
library(tidyr)
library(ggplot2)
library(lme4)
library(AICcmodavg)
library(vegan)
library(flextable)
library(webshot)

requirePackages("DHARMa")

data("stemdata")
metadata <- stemdata
metadata$year <- factor(metadata$year)
metadata$transect <- factor(metadata$transect)

# https://stat.ethz.ch/pipermail/r-sig-mixed-models/2014q4/022870.html
glmerCtrl <- glmerControl(optimizer = c("bobyqa"), optCtrl = list(maxfun=50000))
lmerCtrl <- lmerControl(optimizer = c("bobyqa"), optCtrl = list(maxfun=50000))

mwCache <- getOption("milkweed.cache")
```

```{r}
# Transform data
metadata_usc <- metadata %>% filter(!is.na(h_apical),
                                    !is.na(h_apical.next),
                                    !is.na(herb_avg),
                                    fec.flower == 1, #growth is also only used in the sexual pathway
                                    surv == 1, #plants must survive until september to reproduce in our model
                                    !(year %in% c('2017')),
                                    !(site %in% c('GET', 'GRN'))) %>%   
  mutate(log_herb_avg = log(0.01 + herb_avg), arcsin_herb_avg = asin(sqrt(herb_avg/6)), h_apical_sq = h_apical*h_apical)
                                        
metadata_sc <- metadata_usc %>% mutate_at(.vars = vars(h_apical, h_apical.next, herb_avg, log_herb_avg, arcsin_herb_avg, h_apical_sq),
                                          .funs = funs(as.numeric(scale(.))))

# Get scaling parameters (really just mean and sd)
h_apical_sc <- scale(metadata_usc$h_apical)
h_apical.next_sc <- scale(metadata_usc$h_apical.next)
herb_avg_sc <- scale(metadata_usc$herb_avg)
log_herb_avg_sc = scale(metadata_usc$log_herb_avg)
arcsin_herb_avg_sc = scale(metadata_usc$arcsin_herb_avg)
h_apical_sq_sc = scale(metadata_usc$h_apical_sq)
```

As this is a bona-fide LME, we can do the method mentioned in Zuur.  First, model selection on random effects with REML.

## Random Effects

```{r}
growth.re.site_haThe.year_haThe <- lmer(h_apical.next~h_apical*herb_avg + (h_apical*herb_avg|site/transect)+(h_apical*herb_avg|year), data=metadata_sc, REML=T, control=lmerCtrl)
summary(growth.re.site_haThe.year_haThe)
```

First drop interaction term on site.
```{r}
growth.re.site_haPhe.year_haThe <- lmer(h_apical.next~h_apical*herb_avg + (h_apical+herb_avg|site/transect)+(h_apical*herb_avg|year),data=metadata_sc, REML=T, control=lmerCtrl)
summary(growth.re.site_haPhe.year_haThe)
```

Now drop herbivory on site.
```{r}
growth.re.site_ha.year_haThe <- lmer(h_apical.next~h_apical*herb_avg + (h_apical|site/transect)+(h_apical*herb_avg|year),data=metadata_sc, REML=T, control=lmerCtrl)
summary(growth.re.site_ha.year_haThe)
```

Now drop interaction term on year.
```{r}
growth.re.site_ha.year_haPhe <- lmer(h_apical.next~h_apical*herb_avg + (h_apical|site/transect)+(h_apical+herb_avg|year),data=metadata_sc, REML=T, control=lmerCtrl)
summary(growth.re.site_ha.year_haPhe)
```

Now drop height on year

```{r}
growth.re.site_ha.year_he <- lmer(h_apical.next~h_apical*herb_avg + (h_apical|site/transect)+(herb_avg|year),data=metadata_sc, REML=T, control=lmerCtrl)
summary(growth.re.site_ha.year_he)
```

Winner:
Site: height, year: herbivory

## Fixed effects

```{r}
growth.fe.haThe.site_ha.year_he <- lmer(h_apical.next ~ h_apical*herb_avg + (h_apical|site/transect)+(herb_avg|year), data=metadata_sc, REML=F, control=lmerCtrl)

# 2 terms
growth.fe.haPhe.site_ha.year_he <- lmer(h_apical.next ~ h_apical+herb_avg + (h_apical|site/transect)+(herb_avg|year), data=metadata_sc, REML=F, control=lmerCtrl)

growth.fe.haPhaIhe.site_ha.year_he <- lmer(h_apical.next ~ h_apical+h_apical:herb_avg + (h_apical|site/transect)+(herb_avg|year), data=metadata_sc, REML=F, control=lmerCtrl)

growth.fe.hePhaIhe.site_ha.year_he <- lmer(h_apical.next ~ h_apical:herb_avg + herb_avg + (h_apical|site/transect)+(herb_avg|year), data=metadata_sc, REML=F, control=lmerCtrl)

# 1 term
growth.fe.ha.site_ha.year_he <- lmer(h_apical.next ~ h_apical + (h_apical|site/transect)+(herb_avg|year), data=metadata_sc, REML=F, control=lmerCtrl)

growth.fe.he.site_ha.year_he <- lmer(h_apical.next ~ herb_avg + (h_apical|site/transect)+(herb_avg|year), data=metadata_sc, REML=F, control=lmerCtrl)

growth.fe.haIhe.site_ha.year_he <- lmer(h_apical.next ~ h_apical:herb_avg + (h_apical|site/transect)+(herb_avg|year), data=metadata_sc, REML=F, control=lmerCtrl)

# 0 terms
growth.fe.1.site_ha.year_he <- lmer(h_apical.next ~ 1 + (h_apical|site/transect)+(herb_avg|year), data=metadata_sc, REML=F, control=lmerCtrl)

```

```{r}
growth.fe.AIC <- aictab(list(growth.fe.haThe.site_ha.year_he,
                             growth.fe.haPhe.site_ha.year_he,
                             growth.fe.haPhaIhe.site_ha.year_he,
                             growth.fe.hePhaIhe.site_ha.year_he,
                             growth.fe.ha.site_ha.year_he,
                             growth.fe.he.site_ha.year_he,
                             growth.fe.haIhe.site_ha.year_he,
                             growth.fe.1.site_ha.year_he),
                        modnames = c("Fixed: height*herb",
                                     "Fixed: height+herb",
                                     "Fixed: height+height:herb",
                                     "Fixed: herb+height:herb",
                                     "Fixed: height",
                                     "Fixed: herb",
                                     "Fixed: height:herb",
                                     "Fixed: 1"))
growth.fe.AIC
```

Winner:
```{r}
summary(growth.fe.haPhaIhe.site_ha.year_he)
```

## Model Validation and Diagnostics
Now some diagnostics (aka model validation).
```{r}
par(mfrow=c(2,2))
plot(fitted(growth.fe.haPhaIhe.site_ha.year_he), residuals(growth.fe.haPhaIhe.site_ha.year_he, "deviance"), xlab="Fitted values", ylab="Deviance residuals")
plot(metadata_sc$h_apical, residuals(growth.fe.haPhaIhe.site_ha.year_he, "deviance"), xlab="Apical height", ylab="Deviance residuals")
plot(metadata_sc$herb_avg, residuals(growth.fe.haPhaIhe.site_ha.year_he, "deviance"), xlab="Herbivory average", ylab="Deviance residuals")
par(mfrow=c(1,1))
```

DHARMa Diagnostics
```{r}
growth.simulationOutput = DHARMa::simulateResiduals(fittedModel = growth.fe.haPhaIhe.site_ha.year_he, n=1000)
```

```{r}
DHARMa::plotSimulatedResiduals(growth.simulationOutput)
DHARMa::plotResiduals(metadata_sc$h_apical, growth.simulationOutput$scaledResiduals)
DHARMa::plotResiduals(metadata_sc$herb_avg, growth.simulationOutput$scaledResiduals)
```

Low p-value again may be due to large sample. Plots look ok if you exclude the tails and concentrate on where most of the data is centered, however the shape could be improved.
```{r}
DHARMa::testUniformity(growth.simulationOutput)
```
