---
title: "Supplement - AIC Tables - Flowering"
date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
  compute: TRUE
output: 
  html_document:
    toc: true
---

<!-- Explore caching options (cache.path=mwCache, cache=params$compute) -->

# Initialization

```{r initialize, message=FALSE}
library(milkweed)
library(dplyr)
library(tidyr)
library(ggplot2)
library(lme4)
library(AICcmodavg)
library(vegan)
library(flextable)
library(webshot)

requirePackages("DHARMa")

data("stemdata")
metadata <- stemdata
metadata$year <- factor(metadata$year)
metadata$transect <- factor(metadata$transect)

# https://stat.ethz.ch/pipermail/r-sig-mixed-models/2014q4/022870.html
glmerCtrl <- glmerControl(optimizer = c("bobyqa"), optCtrl = list(maxfun=50000))
lmerCtrl <- lmerControl(optimizer = c("bobyqa"), optCtrl = list(maxfun=50000))

mwCache <- getOption("milkweed.cache")
```

```{r flowering scaling}
metadata_usc <- metadata %>% filter(!is.na(h_apical),
                                    !is.na(herb_avg),
                                    !is.na(fec.flower),
                                    !(year %in% c('2017')),
                                    !(site %in% c('GET', 'GRN'))
                                    )

metadata_sc <- metadata_usc %>% mutate_at(.vars = vars(h_apical, herb_avg),
                                          .funs = ~ as.numeric(scale(.))) 

# Get scaling parameters (really just mean and sd)
h_apical_sc <- scale(metadata_usc$h_apical)
herb_avg_sc <- scale(metadata_usc$herb_avg)
```

# Random Effects

## Starting with site

Use nAGQ = 0 for quick approximations, but less exact form of parameter estimation.
```{r flowering random effects with site}
compute <- params$compute
savefile <- "aictabs_F_RE_Site.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 3 terms
  flower.re.site_haThe.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 2 terms
  flower.re.site_hePhaIhe.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (herb_avg + h_apical:herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_haPhaIhe.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical + h_apical:herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_haPhe.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical + herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 1 term
  flower.re.site_he.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_ha.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_haIhe.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical:herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 0 terms
  flower.re.site_1.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (1|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  save(flower.re.site_haThe.year_haThe,
       flower.re.site_hePhaIhe.year_haThe,
       flower.re.site_haPhaIhe.year_haThe,
       flower.re.site_haPhe.year_haThe,
       flower.re.site_he.year_haThe,
       flower.re.site_ha.year_haThe,
       flower.re.site_haIhe.year_haThe,
       flower.re.site_1.year_haThe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r flowering AIC table with site}
aictab(list(flower.re.site_haThe.year_haThe,
            flower.re.site_hePhaIhe.year_haThe,
            flower.re.site_haPhaIhe.year_haThe,
            flower.re.site_haPhe.year_haThe,
            flower.re.site_he.year_haThe,
            flower.re.site_ha.year_haThe,
            flower.re.site_haIhe.year_haThe,
            flower.re.site_1.year_haThe),
       modnames = c("Site: height*herb", 
                    "Site: herb + height:herb", 
                    "Site: height + height:herb", 
                    "Site: height + herb",
                    "Site: herb",
                    "Site: height",
                    "Site: height:herb",
                    "Site: 1"))
```

Now do year with height|site 

```{r}
compute <- params$compute
savefile <- "aictabs_F_RE_Site_Year_1.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 3 terms
  flower.re.site_ha.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 2 terms
  flower.re.site_ha.year_hePhaIhe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical:herb_avg + herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_ha.year_haPhaIhe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_ha.year_haPhe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 1 term
  flower.re.site_ha.year_he <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_ha.year_ha <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_ha.year_haIhe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 0 terms
  flower.re.site_ha.year_1 <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (1|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  save(flower.re.site_ha.year_haThe,
       flower.re.site_ha.year_hePhaIhe,
       flower.re.site_ha.year_haPhaIhe,
       flower.re.site_ha.year_haPhe,
       flower.re.site_ha.year_he,
       flower.re.site_ha.year_ha,
       flower.re.site_ha.year_haIhe,
       flower.re.site_ha.year_1, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```



```{r}
aictab(list(flower.re.site_ha.year_haThe,
       flower.re.site_ha.year_hePhaIhe,
       flower.re.site_ha.year_haPhaIhe,
       flower.re.site_ha.year_haPhe,
       flower.re.site_ha.year_he,
       flower.re.site_ha.year_ha,
       flower.re.site_ha.year_haIhe,
       flower.re.site_ha.year_1),
       modnames = c("Site: height, Year: height*herb", 
                    "Site: height, Year: herb + height:herb", 
                    "Site: height, Year: height + height:herb", 
                    "Site: height, Year: height + herb",
                    "Site: height, Year: herb",
                    "Site: height, Year: height",
                    "Site: height, Year: height",
                    "Site: height, Year: 1"))
```

Winner:
Site: height, Year: height*herb


## Starting with year

Use nAGQ = 0 for quick approximations, but less exact form of parameter estimation.
```{r}
compute <- params$compute
savefile <- "aictabs_F_RE_Year.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 3 terms
  flower.re.site_haThe.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 2 terms
  flower.re.site_haThe.year_haPhe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_haThe.year_haPhaIhe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_haThe.year_haIhePhe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical:herb_avg + herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 1 term
  flower.re.site_haThe.year_ha <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_haThe.year_he <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_haThe.year_haIhe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 0 terms
  flower.re.site_haThe.year_1 <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (1|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  save(flower.re.site_haThe.year_haThe,
       flower.re.site_haThe.year_haIhePhe,
       flower.re.site_haThe.year_haPhaIhe,
       flower.re.site_haThe.year_haPhe,
       flower.re.site_haThe.year_he,
       flower.re.site_haThe.year_ha,
       flower.re.site_haThe.year_haIhe,
       flower.re.site_haThe.year_1, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r flowering AIC table with site}
aictab(list(flower.re.site_haThe.year_haThe,
       flower.re.site_haThe.year_haIhePhe,
       flower.re.site_haThe.year_haPhaIhe,
       flower.re.site_haThe.year_haPhe,
       flower.re.site_haThe.year_he,
       flower.re.site_haThe.year_ha,
       flower.re.site_haThe.year_haIhe,
       flower.re.site_haThe.year_1),
       modnames = c("Year: height*herb", 
                    "Year: herb + height:herb", 
                    "Year: height + height:herb", 
                    "Year: height + herb",
                    "Year: herb",
                    "Year: height",
                    "Year: height:herb",
                    "Year: 1"))
```

Now do site with height*herb|year (already done above) and height+height:herb|year.

```{r}
compute <- params$compute
savefile <- "aictabs_F_RE_Year_Site.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 3 terms
  flower.re.site_haThe.year_haPhaIhe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 2 terms
  flower.re.site_hePhaIhe.year_haPhaIhe <- glmer(fec.flower ~ h_apical*herb_avg + (herb_avg + h_apical:herb_avg|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_haPhaIhe.year_haPhaIhe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical + h_apical:herb_avg|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_haPhe.year_haPhaIhe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical + herb_avg|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 1 term
  flower.re.site_he.year_haPhaIhe <- glmer(fec.flower ~ h_apical*herb_avg + (herb_avg|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_ha.year_haPhaIhe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_haIhe.year_haPhaIhe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical:herb_avg|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 0 terms
  flower.re.site_1.year_haPhaIhe <- glmer(fec.flower ~ h_apical*herb_avg + (1|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  save(flower.re.site_haThe.year_haPhaIhe,
       flower.re.site_hePhaIhe.year_haPhaIhe,
       flower.re.site_haPhaIhe.year_haPhaIhe,
       flower.re.site_haPhe.year_haPhaIhe,
       flower.re.site_he.year_haPhaIhe,
       flower.re.site_ha.year_haPhaIhe,
       flower.re.site_haIhe.year_haPhaIhe,
       flower.re.site_1.year_haPhaIhe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r}
compute <- params$compute
savefile <- "aictabs_F_RE_Site.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 3 terms
  flower.re.site_haThe.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 2 terms
  flower.re.site_hePhaIhe.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (herb_avg + h_apical:herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_haPhaIhe.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical + h_apical:herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_haPhe.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical + herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 1 term
  flower.re.site_he.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_ha.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_haIhe.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical:herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 0 terms
  flower.re.site_1.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (1|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  save(flower.re.site_haThe.year_haThe,
       flower.re.site_hePhaIhe.year_haThe,
       flower.re.site_haPhaIhe.year_haThe,
       flower.re.site_haPhe.year_haThe,
       flower.re.site_he.year_haThe,
       flower.re.site_ha.year_haThe,
       flower.re.site_haIhe.year_haThe,
       flower.re.site_1.year_haThe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r}
aictab(list(flower.re.site_haThe.year_haPhaIhe,
       flower.re.site_hePhaIhe.year_haPhaIhe,
       flower.re.site_haPhaIhe.year_haPhaIhe,
       flower.re.site_haPhe.year_haPhaIhe,
       flower.re.site_he.year_haPhaIhe,
       flower.re.site_ha.year_haPhaIhe,
       flower.re.site_haIhe.year_haPhaIhe,
       flower.re.site_1.year_haPhaIhe,
       flower.re.site_haThe.year_haThe,
       flower.re.site_hePhaIhe.year_haThe,
       flower.re.site_haPhaIhe.year_haThe,
       flower.re.site_haPhe.year_haThe,
       flower.re.site_he.year_haThe,
       flower.re.site_ha.year_haThe,
       flower.re.site_haIhe.year_haThe,
       flower.re.site_1.year_haThe),
       modnames = c("Site: height*herb, Year: height+height:herb", 
                    "Site: herb + height:herb, Year: height+height:herb", 
                    "Site: height + height:herb, Year: height+height:herb", 
                    "Site: height + herb, Year: height+height:herb",
                    "Site: herb, Year: height+height:herb",
                    "Site: height, Year: height+height:herb",
                    "Site: height:herb, Year: height+height:herb",
                    "Site: 1, Year: height+height:herb",
                    "Site: height*herb, Year: height*herb", 
                    "Site: herb + height:herb, Year: height*herb", 
                    "Site: height + height:herb, Year: height*herb", 
                    "Site: height + herb, Year: height*herb",
                    "Site: herb, Year: height*herb",
                    "Site: height, Year: height*herb",
                    "Site: height:herb, Year: height*herb",
                    "Site: 1, Year: height*herb"))
```

Winners: 
Site: height, Year: height*herb


## Winner for both

Site: height, Year: height*herb

### Singularity check


```{r}
compute <- params$compute
savefile <- "aictabs_F_Sing_1.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  flower.fe.haThe.re.site_ha.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)

  save(flower.fe.haThe.re.site_ha.year_haThe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
rePCA(flower.fe.haThe.re.site_ha.year_haThe)
```

Both site and year have parameter outputs as 0s. Let's first try dropping height on site.

```{r}
compute <- params$compute
savefile <- "aictabs_F_Sing_2.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  flower.fe.haThe.re.site_1.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (1|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)

  save(flower.fe.haThe.re.site_1.year_haThe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
rePCA(flower.fe.haThe.re.site_1.year_haThe)
```

Still singular. Let's try reducing the interaction term on year.

```{r}
compute <- params$compute
savefile <- "aictabs_F_Sing_3.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  flower.fe.haThe.re.site_1.year_haPhe <- glmer(fec.flower ~ h_apical*herb_avg + (1|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)

  save(flower.fe.haThe.re.site_1.year_haPhe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
rePCA(flower.fe.haThe.re.site_1.year_haPhe)
```

Let's drop herbivory.

```{r}
compute <- params$compute
savefile <- "aictabs_F_Sing_4.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  flower.fe.haThe.re.site_1.year_ha <- glmer(fec.flower ~ h_apical*herb_avg + (1|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)

  save(flower.fe.haThe.re.site_1.year_ha, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
rePCA(flower.fe.haThe.re.site_1.year_ha)
```
What if we started by dropping the interaction term instead?

```{r}
compute <- params$compute
savefile <- "aictabs_F_Sing_5.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  flower.fe.haThe.re.site_ha.year_haPhe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)

  save(flower.fe.haThe.re.site_ha.year_haPhe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
rePCA(flower.fe.haThe.re.site_ha.year_haPhe)
```
Now drop herbivory on year.

```{r}
compute <- params$compute
savefile <- "aictabs_F_Sing_6.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  flower.fe.haThe.re.site_ha.year_ha <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)

  save(flower.fe.haThe.re.site_ha.year_ha, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
rePCA(flower.fe.haThe.re.site_ha.year_ha)
```


Would have to drop height on site, same result as before. In either case...

Winner:
site: 1, year: height

# Fixed Effects

```{r flowering fixed effects}
compute <- params$compute
savefile <- "aictabs_F_FE.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 2 terms
  flower.fe.haPhe.re.site_1.year_ha <- glmer(fec.flower ~ h_apical+herb_avg + (1|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  flower.fe.haPhaIhe.re.site_1.year_ha <- glmer(fec.flower ~ h_apical+h_apical:herb_avg + (1|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  flower.fe.hePhaIhe.re.site_1.year_ha <- glmer(fec.flower ~ herb_avg+h_apical:herb_avg + (1|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  # 1 term
  flower.fe.ha.re.site_1.year_ha <- glmer(fec.flower ~ h_apical + (1|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  flower.fe.he.re.site_1.year_ha <- glmer(fec.flower ~ herb_avg + (1|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  flower.fe.haIhe.re.site_1.year_ha <- glmer(fec.flower ~ h_apical:herb_avg + (1|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  # 0 terms
  flower.fe.1.re.site_1.year_ha <- glmer(fec.flower ~ 1 + (1|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  save(flower.fe.haThe.re.site_1.year_ha,
       flower.fe.hePhaIhe.re.site_1.year_ha,
       flower.fe.haPhaIhe.re.site_1.year_ha,
       flower.fe.haPhe.re.site_1.year_ha,
       flower.fe.he.re.site_1.year_ha,
       flower.fe.ha.re.site_1.year_ha,
       flower.fe.haIhe.re.site_1.year_ha,
       flower.fe.1.re.site_1.year_ha, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r flowering fixed effects AIC table}
aictab(list(flower.fe.haThe.re.site_1.year_ha,
       flower.fe.hePhaIhe.re.site_1.year_ha,
       flower.fe.haPhaIhe.re.site_1.year_ha,
       flower.fe.haPhe.re.site_1.year_ha,
       flower.fe.he.re.site_1.year_ha,
       flower.fe.ha.re.site_1.year_ha,
       flower.fe.haIhe.re.site_1.year_ha,
       flower.fe.1.re.site_1.year_ha),
       modnames = c("Fixed: height*herb", 
                    "Fixed: herb + height:herb", 
                    "Fixed: height + height:herb", 
                    "Fixed: height + herb",
                    "Fixed: herb",
                    "Fixed: height",
                    "Fixed: height:herb",
                    "Fixed: 1"))
```
Winner: 
```{r flowering winner}
summary(flower.fe.haThe.re.site_1.year_ha)
```

## Model Diagnostics

Now some diagnostics (aka model validation). Creating the standard residual plots. Interpretting these plots is questionable for a non-linear model fit, so we will also imploy non-linear diagnostics next.
```{r}
par(mfrow=c(2,2))
plot(fitted(flower.fe.haThe.re.site_1.year_ha), residuals(flower.fe.haThe.re.site_1.year_ha, "deviance"), xlab="Fitted values", ylab="Deviance residuals")
plot(metadata_sc$h_apical, residuals(flower.fe.haThe.re.site_1.year_ha, "deviance"), xlab="Apical height", ylab="Deviance residuals")
plot(metadata_sc$herb_avg, residuals(flower.fe.haThe.re.site_1.year_ha, "deviance"), xlab="Herbivory average", ylab="Deviance residuals")
par(mfrow=c(1,1))
```

DHARMa package diagnostics for non-linear, hierarchical, mixed models. This simulates new data from the fitted model for the predictor variable combination of each observation. Then for each observation, calculates the empirical cumulative density function for the simulated data, which describes the expected spread for an observation at the respective point in predictor space, conditional on the fitted model. The residual is defined as the value of the empirical density function at the value of the observed data (DHARMa package vignette).
```{r}
flower.simulationOutput <- DHARMa::simulateResiduals(fittedModel = flower.fe.haThe.re.site_1.year_ha, n=1000) #simulate data, n set to 1000 for high precision
```

```{r}
# DHARMa diagnostic plot, then plots of residuals against the predictor variables independently, we want flat horizontal lines at 0.25, 0.5, and 0.75 in a perfect world.
DHARMa::plotSimulatedResiduals(flower.simulationOutput)
DHARMa::plotResiduals(metadata_sc$h_apical, flower.simulationOutput$scaledResiduals)
DHARMa::plotResiduals(metadata_sc$herb_avg, flower.simulationOutput$scaledResiduals)
```
```{r}
# tests to see if the residuals fit the expected distribution
DHARMa::testUniformity(flower.simulationOutput)
```

Plots look great! Looks like the final model is a good fit. The Uniformity Test is probably failing since we have such a large sample size and it is not a particularly strong test.

AIC Plots

## Visualizations

Create model class
```{r}
scaled <- list(h_apical = h_apical_sc, herb_avg = herb_avg_sc)
flower.fit <- mwMod(list(mdl = flower.fe.haThe.re.site_1.year_ha, vars = c("h_apical", "herb_avg"), scaled = scaled))
checkPars(flower.fit) # Check parameters
```

```{r}
flower.fit$pars$scaled
```

Unscaled parameters across site:
```{r}
flower.fit$pars$unscaled
```

Let's plot full data.
```{r, eval=F}
# Create plot data for prediction curves
plotdata <- metadata_usc %>% 
  group_by(site) %>% 
  summarize(mean_herb_avg = mean(herb_avg),
            min_h_apical = min(h_apical),
            max_h_apical = max(h_apical)) %>%
  add_row(site = "Bertha",
          mean_herb_avg = mean(metadata_usc$herb_avg, na.rm=T),
          min_h_apical = min(metadata_usc$h_apical, na.rm=T),
          max_h_apical = max(metadata_usc$h_apical, na.rm=T))

# Create prediction curves
N <- 100
suppressWarnings( # Hiding the follow warnings: (1) Unequal factor levels: coercing to character and (2) binding character and factor vector, coercing into character vector
  curves <- bind_rows(
    lapply(as.vector(plotdata$site), function(site) {
      i <- which(plotdata$site == site)
      data.frame(
        site = site,
        h_apical = seq(plotdata$min_h_apical[i], plotdata$max_h_apical[i], length.out = N),
        herb_avg = plotdata$mean_herb_avg[i],
        fec.flower = predict(
          flower.fit,
          type = site,
          newdata = data.frame(
            h_apical = seq(plotdata$min_h_apical[i], plotdata$max_h_apical[i], length.out = N),
            herb_avg = rep(plotdata$mean_herb_avg[i], N)
          )
        )
      )
    })
  )
)

flower.plot <- metadata_usc %>% 
  ggplot(aes(x = h_apical, 
             y = fec.flower)) + 
  geom_jitter(height = 0.1, 
              alpha = 0.3) +
  facet_wrap(~ site)

flower.plot + 
  geom_line(data = curves %>% filter(site != "Bertha")) + 
  facet_wrap(~ site)
```
