---
title: "Supplement - AIC Tables"
date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
  compute: TRUE
output: 
  html_document:
    toc: true
---

<!-- Explore caching options (cache.path=mwCache, cache=params$compute) -->

# Initialization

```{r initialize, message=FALSE}
library(milkweed)
library(dplyr)
library(tidyr)
library(ggplot2)
library(lme4)
library(AICcmodavg)
library(vegan)
library(flextable)
library(webshot)

requirePackages("DHARMa")

data("stemdata")
metadata <- stemdata
metadata$year <- factor(metadata$year)
metadata$transect <- factor(metadata$transect)

# https://stat.ethz.ch/pipermail/r-sig-mixed-models/2014q4/022870.html
glmerCtrl <- glmerControl(optimizer = c("bobyqa"), optCtrl = list(maxfun=50000))
lmerCtrl <- lmerControl(optimizer = c("bobyqa"), optCtrl = list(maxfun=50000))

mwCache <- getOption("milkweed.cache")
```

# Flowering

```{r flowering scaling}
metadata_usc <- metadata %>% filter(!is.na(h_apical),
                                    !is.na(herb_avg),
                                    !is.na(fec.flower))

metadata_sc <- metadata_usc %>% mutate_at(.vars = vars(h_apical, herb_avg),
                                          .funs = ~ as.numeric(scale(.))) 

# Get scaling parameters (really just mean and sd)
h_apical_sc <- scale(metadata_usc$h_apical)
herb_avg_sc <- scale(metadata_usc$herb_avg)
```

## Random Effects - Starting with Site

Use nAGQ = 0 for quick approximations, but less exact form of parameter estimation.
```{r flowering random effects with site}
compute <- params$compute
savefile <- "aictabs_F_RE_Site.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 3 terms
  flower.re.site_haThe.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 2 terms
  flower.re.site_hePhaIhe.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (herb_avg + h_apical:herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_haPhaIhe.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical + h_apical:herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_haPhe.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical + herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 1 term
  flower.re.site_he.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_ha.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_haIhe.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical:herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 0 terms
  flower.re.site_1.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (1|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  save(flower.re.site_haThe.year_haThe,
       flower.re.site_hePhaIhe.year_haThe,
       flower.re.site_haPhaIhe.year_haThe,
       flower.re.site_haPhe.year_haThe,
       flower.re.site_he.year_haThe,
       flower.re.site_ha.year_haThe,
       flower.re.site_haIhe.year_haThe,
       flower.re.site_1.year_haThe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r flowering AIC table with site}
aictab(list(flower.re.site_haThe.year_haThe,
            flower.re.site_hePhaIhe.year_haThe,
            flower.re.site_haPhaIhe.year_haThe,
            flower.re.site_haPhe.year_haThe,
            flower.re.site_he.year_haThe,
            flower.re.site_ha.year_haThe,
            flower.re.site_haIhe.year_haThe,
            flower.re.site_1.year_haThe),
       modnames = c("Site: height*herb", 
                    "Site: herb + height:herb", 
                    "Site: height + height:herb", 
                    "Site: height + herb",
                    "Site: herb",
                    "Site: height",
                    "Site: height:herb",
                    "Site: 1"))
```

Height wins!  Let's move to year:
```{r flowering with year}
compute <- params$compute
savefile <- "aictabs_F_RE_Year.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 2 terms
  flower.re.site_ha.year_haPhe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_ha.year_haPhaIhe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_ha.year_hePhaIhe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (herb_avg+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 1 term
  flower.re.site_ha.year_he <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_ha.year_ha <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.site_ha.year_haIhe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 0 terms
  flower.re.site_ha.year_1 <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (1|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  save(flower.re.site_ha.year_haThe,
       flower.re.site_ha.year_hePhaIhe,
       flower.re.site_ha.year_haPhaIhe,
       flower.re.site_ha.year_haPhe,
       flower.re.site_ha.year_he,
       flower.re.site_ha.year_ha,
       flower.re.site_ha.year_haIhe,
       flower.re.site_ha.year_1, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r flowering AIC table with year}
aictab(list(flower.re.site_ha.year_haThe,
            flower.re.site_ha.year_hePhaIhe,
            flower.re.site_ha.year_haPhaIhe,
            flower.re.site_ha.year_haPhe,
            flower.re.site_ha.year_he,
            flower.re.site_ha.year_ha,
            flower.re.site_ha.year_haIhe,
            flower.re.site_ha.year_1),
       modnames = c("Year: height*herb", 
                    "Year: herb + height:herb", 
                    "Year: height + height:herb", 
                    "Year: height + herb",
                    "Year: herb",
                    "Year: height",
                    "Year: height:herb",
                    "Year: 1"))
```

```{r flowering singularity check}
compute <- params$compute
savefile <- "aictabs_F_Sing_1.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  flower.fe.haThe.re.site_ha.year_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  rePCA(flower.fe.haThe.re.site_ha.year_haThe)

  save(flower.fe.haThe.re.site_ha.year_haThe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

We have a singularity issue.  Looks like issue is in the year random effect.  Let's drop the interaction term.
```{r flowering singularity adjustment}
compute <- params$compute
savefile <- "aictabs_F_Sing_2.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  flower.fe.haThe.re.site_ha.year_haPhe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  rePCA(flower.fe.haThe.re.site_ha.year_haPhe)

  save(flower.fe.haThe.re.site_ha.year_haPhe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

Still have a problem, but now in site.  Let's drop height:
```{r flowering singularity persisting}
compute <- params$compute
savefile <- "aictabs_f_Sing_3.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  flower.fe.haThe.re.site_1.year_haPhe <- glmer(fec.flower ~ h_apical*herb_avg + (1|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  rePCA(flower.fe.haThe.re.site_1.year_haPhe)
  
  save(flower.fe.haThe.re.site_1.year_haPhe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

## Random Effects - Starting with Year

Use nAGQ = 0 for quick approximations, but less exact form of parameter estimation.
```{r flowering random effects with year}
compute <- params$compute
savefile <- "aictabs_F_RE_Year_First.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 3 terms
  flower.re.year_haThe.site_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 2 terms
  flower.re.year_hePhaIhe.site_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (herb_avg + h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.year_haPhaIhe.site_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical + h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.year_haPhe.site_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical + herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 1 term
  flower.re.year_he.site_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.year_ha.site_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  flower.re.year_haIhe.site_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 0 terms
  flower.re.year_1.site_haThe <- glmer(fec.flower ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (1|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  save(flower.re.year_haThe.site_haThe,
       flower.re.year_hePhaIhe.site_haThe,
       flower.re.year_haPhaIhe.site_haThe,
       flower.re.year_haPhe.site_haThe,
       flower.re.year_he.site_haThe,
       flower.re.year_ha.site_haThe,
       flower.re.year_haIhe.site_haThe,
       flower.re.year_1.site_haThe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r flowering random effects year AIC table }
aictab(list(flower.re.year_haThe.site_haThe,
            flower.re.year_hePhaIhe.site_haThe,
            flower.re.year_haPhaIhe.site_haThe,
            flower.re.year_haPhe.site_haThe,
            flower.re.year_he.site_haThe,
            flower.re.year_ha.site_haThe,
            flower.re.year_haIhe.site_haThe,
            flower.re.year_1.site_haThe),
       modnames = c("Year: height*herb", 
                    "Year: herb + height:herb", 
                    "Year: height + height:herb", 
                    "Year: height + herb",
                    "Year: herb",
                    "Year: height",
                    "Year: height:herb",
                    "Year: 1"))
```

## Fixed Effects

```{r flowering fixed effects}
compute <- params$compute
savefile <- "aictabs_F_FE.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 2 terms
  flower.fe.haPhe.re.site_1.year_haPhe <- glmer(fec.flower ~ h_apical+herb_avg + (1|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  flower.fe.haPhaIhe.re.site_1.year_haPhe <- glmer(fec.flower ~ h_apical+h_apical:herb_avg + (1|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  flower.fe.hePhaIhe.re.site_1.year_haPhe <- glmer(fec.flower ~ herb_avg+h_apical:herb_avg + (1|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  # 1 term
  flower.fe.ha.re.site_1.year_haPhe <- glmer(fec.flower ~ h_apical + (1|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  flower.fe.he.re.site_1.year_haPhe <- glmer(fec.flower ~ herb_avg + (1|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  flower.fe.haIhe.re.site_1.year_haPhe <- glmer(fec.flower ~ h_apical:herb_avg + (1|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  # 0 terms
  flower.fe.1.re.site_1.year_haPhe <- glmer(fec.flower ~ 1 + (1|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  save(flower.fe.haThe.re.site_1.year_haPhe,
       flower.fe.hePhaIhe.re.site_1.year_haPhe,
       flower.fe.haPhaIhe.re.site_1.year_haPhe,
       flower.fe.haPhe.re.site_1.year_haPhe,
       flower.fe.he.re.site_1.year_haPhe,
       flower.fe.ha.re.site_1.year_haPhe,
       flower.fe.haIhe.re.site_1.year_haPhe,
       flower.fe.1.re.site_1.year_haPhe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r flowering fixed effects AIC table}
aictab(list(flower.fe.haThe.re.site_1.year_haPhe,
            flower.fe.hePhaIhe.re.site_1.year_haPhe,
            flower.fe.haPhaIhe.re.site_1.year_haPhe,
            flower.fe.haPhe.re.site_1.year_haPhe,
            flower.fe.he.re.site_1.year_haPhe,
            flower.fe.ha.re.site_1.year_haPhe,
            flower.fe.haIhe.re.site_1.year_haPhe,
            flower.fe.1.re.site_1.year_haPhe),
       modnames = c("Fixed: height*herb", 
                    "Fixed: herb + height:herb", 
                    "Fixed: height + height:herb", 
                    "Fixed: height + herb",
                    "Fixed: herb",
                    "Fixed: height",
                    "Fixed: height:herb",
                    "Fixed: 1"))
```

Winner:
```{r flowering winner}
summary(flower.fe.haThe.re.site_1.year_haPhe)
```

## Model Diagnostics

Now some diagnostics (aka model validation). Creating the standard residual plots. Interpretting these plots is questionable for a non-linear model fit, so we will also imploy non-linear diagnostics next.
```{r}
par(mfrow=c(2,2))
plot(fitted(flower.fe.haThe.re.site_1.year_haPhe), residuals(flower.fe.haThe.re.site_1.year_haPhe, "deviance"), xlab="Fitted values", ylab="Deviance residuals")
plot(metadata_sc$h_apical, residuals(flower.fe.haThe.re.site_1.year_haPhe, "deviance"), xlab="Apical height", ylab="Deviance residuals")
plot(metadata_sc$herb_avg, residuals(flower.fe.haThe.re.site_1.year_haPhe, "deviance"), xlab="Herbivory average", ylab="Deviance residuals")
par(mfrow=c(1,1))
```

DHARMa package diagnostics for non-linear, hierarchical, mixed models. This simulates new data from the fitted model for the predictor variable combination of each observation. Then for each observation, calculates the empirical cumulative density function for the simulated data, which describes the expected spread for an observation at the respective point in predictor space, conditional on the fitted model. The residual is defined as the value of the empirical density function at the value of the observed data (DHARMa package vignette).
```{r}
flower.simulationOutput <- DHARMa::simulateResiduals(fittedModel = flower.fe.haThe.re.site_1.year_haPhe, n=1000) #simulate data, n set to 1000 for high precision
```

```{r}
# DHARMa diagnostic plot, then plots of residuals against the predictor variables independently, we want flat horizontal lines at 0.25, 0.5, and 0.75 in a perfect world.
DHARMa::plotSimulatedResiduals(flower.simulationOutput)
DHARMa::plotResiduals(metadata_sc$h_apical, flower.simulationOutput$scaledResiduals)
DHARMa::plotResiduals(metadata_sc$herb_avg, flower.simulationOutput$scaledResiduals)
```

```{r}
# tests to see if the residuals fit the expected distribution
DHARMa::testUniformity(flower.simulationOutput)
```
Plots look great! Looks like the final model is a good fit. The Uniformity Test is probably failing since we have such a large sample size and it is not a particularly strong test. It does have a relatively large p-value compared to some other decent fits we've seen.

## Create AIC Tables

### Random Effect: Site

Let's create the full table for publication:
```{r flowering winner AIC table}
f.re.site.AIC <- aictab(list(flower.re.site_haThe.year_haThe,
            flower.re.site_hePhaIhe.year_haThe,
            flower.re.site_haPhaIhe.year_haThe,
            flower.re.site_haPhe.year_haThe,
            flower.re.site_he.year_haThe,
            flower.re.site_ha.year_haThe,
            flower.re.site_haIhe.year_haThe,
            flower.re.site_1.year_haThe),
       modnames = c("Site: height*herb", 
                    "Site: herb + height:herb", 
                    "Site: height + height:herb", 
                    "Site: height + herb",
                    "Site: herb",
                    "Site: height",
                    "Site: height:herb",
                    "Site: 1"))
f.re.site.AIC
```

Let's format this puppy:
```{r flowering AIC table formatting}
ft <- flextable(f.re.site.AIC) %>%
  add_header(Modnames = "Flowering: Site Random Effect") %>%
  fontsize(part = "header", size = 12) %>%
  set_header_labels(Modnames = "Model") %>% 
  bg(i = 1, bg = "#dedede") %>% 
  width(j = ~ Modnames, width = 2.6) %>%
  set_formatter(
    K = function(x) sprintf("%d", x)
  )
ft
```

Now save as image:
```{r flowering save image}
# create an Rmd file ----
rmd_name <- tempfile(fileext = ".Rmd")
cat("```{r echo=FALSE, ft.shadow=FALSE}\nft\n```", file = rmd_name)
# render as an html file ----
html_name <- tempfile(fileext = ".html")
rmarkdown::render(rmd_name, output_format = "html_document", output_file = html_name)
# get a png from the html file with webshot ----
webshot(html_name, zoom = 2, file = "floweringRE_Site_AIC.png", 
        selector = "body > div.container-fluid.main-container > div.tabwid > table")
```

### Random Effect: Year

Let's create the full table for publication:
```{r flowering full year AIC table}
f.re.year.AIC <- aictab(list(flower.re.site_ha.year_haThe,
            flower.re.site_ha.year_hePhaIhe,
            flower.re.site_ha.year_haPhaIhe,
            flower.re.site_ha.year_haPhe,
            flower.re.site_ha.year_he,
            flower.re.site_ha.year_ha,
            flower.re.site_ha.year_haIhe,
            flower.re.site_ha.year_1),
       modnames = c("Year: height*herb", 
                    "Year: herb + height:herb", 
                    "Year: height + height:herb", 
                    "Year: height + herb",
                    "Year: herb",
                    "Year: height",
                    "Year: height:herb",
                    "Year: 1"))
f.re.year.AIC
```

Let's format this puppy:
```{r flowering year AIC formatting}
ft <- flextable(f.re.year.AIC) %>%
  add_header(Modnames = "Flowering: Year Random Effect") %>%
  fontsize(part = "header", size = 12) %>%
  set_header_labels(Modnames = "Model") %>% 
  bg(i = 1, bg = "#dedede") %>% 
  width(j = ~ Modnames, width = 2.6) %>%
  set_formatter(
    K = function(x) sprintf("%d", x)
  )
ft
```

Now save as image:
```{r flowering year save}
# create an Rmd file ----
rmd_name <- tempfile(fileext = ".Rmd")
cat("```{r echo=FALSE, ft.shadow=FALSE}\nft\n```", file = rmd_name)
# render as an html file ----
html_name <- tempfile(fileext = ".html")
rmarkdown::render(rmd_name, output_format = "html_document", output_file = html_name)
# get a png from the html file with webshot ----
webshot(html_name, zoom = 2, file = "floweringRE_Year_AIC.png", 
        selector = "body > div.container-fluid.main-container > div.tabwid > table")
```

### Dealing with singularity

```{r flowering singularity thingy}
f.singularity.AIC <- aictab(list(flower.fe.haThe.re.site_ha.year_haThe,
                                 flower.fe.haThe.re.site_ha.year_haPhe,
                                 flower.fe.haThe.re.site_1.year_haPhe),
                            modnames = c("(S) Site: height, Year: h_apical*height",
                                         "(S) Site: height, Year: h_apical+height",
                                         "(NS) Site: 1, Year: h_apical+height"))
f.singularity.AIC
```

Let's format this puppy:
```{r flowering format singularity table}
ft <- flextable(f.singularity.AIC) %>%
  add_header(Modnames = "Flowering: Singularity Adjustments") %>%
  fontsize(part = "header", size = 12) %>%
  set_header_labels(Modnames = "Model") %>% 
  bg(i = 3, bg = "#dedede") %>% 
  width(j = ~ Modnames, width = 2.6) %>%
  set_formatter(
    K = function(x) sprintf("%d", x)
  )
ft
```

Now save as image:
```{r flowering save singularity thingy table}
# create an Rmd file ----
rmd_name <- tempfile(fileext = ".Rmd")
cat("```{r echo=FALSE}\nft\n```", file = rmd_name)
# render as an html file ----
html_name <- tempfile(fileext = ".html")
rmarkdown::render(rmd_name, output_format = "html_document", output_file = html_name)
# get a png from the html file with webshot ----
# webshot(html_name, zoom = 2, file = "floweringRE_Singularity_AIC.png", 
#         selector = "body > div.container-fluid.main-container > div.tabwid > table")
```

### Fixed Effects

Let's create the full table for publication:
```{r flowering winner fixed effects AIC table}
f.fe.AIC <- aictab(list(flower.fe.haThe.re.site_1.year_haPhe,
            flower.fe.hePhaIhe.re.site_1.year_haPhe,
            flower.fe.haPhaIhe.re.site_1.year_haPhe,
            flower.fe.haPhe.re.site_1.year_haPhe,
            flower.fe.he.re.site_1.year_haPhe,
            flower.fe.ha.re.site_1.year_haPhe,
            flower.fe.haIhe.re.site_1.year_haPhe,
            flower.fe.1.re.site_1.year_haPhe),
       modnames = c("Fixed: height*herb", 
                    "Fixed: herb + height:herb", 
                    "Fixed: height + height:herb", 
                    "Fixed: height + herb",
                    "Fixed: herb",
                    "Fixed: height",
                    "Fixed: height:herb",
                    "Fixed: 1"))
f.fe.AIC
```

Let's format this puppy:
```{r f.fe.AIC formatting}
ft <- flextable(f.fe.AIC) %>%
  add_header(Modnames = "Flowering: Fixed Effects") %>%
  fontsize(part = "header", size = 12) %>%
  set_header_labels(Modnames = "Model") %>% 
  bg(i = 2, bg = "#dedede") %>% 
  width(j = ~ Modnames, width = 2.6) %>%
  set_formatter(
    K = function(x) sprintf("%d", x)
  )
ft
```

Now save as image:
```{r f.fe.AIC saving}
# create an Rmd file ----
rmd_name <- tempfile(fileext = ".Rmd")
cat("```{r echo=FALSE}\nft\n```", file = rmd_name)
# render as an html file ----
html_name <- tempfile(fileext = ".html")
rmarkdown::render(rmd_name, output_format = "html_document", output_file = html_name)
# get a png from the html file with webshot ----
# webshot(html_name, zoom = 2, file = "floweringFE_AIC.png", 
#         selector = "body > div.container-fluid.main-container > div.tabwid > table")
```

## Visualizations

Create model class
```{r}
scaled <- list(h_apical = h_apical_sc, herb_avg = herb_avg_sc)
flower.fit <- mwMod(list(mdl = flower.fe.haThe.re.site_1.year_haPhe, vars = c("h_apical", "herb_avg"), scaled = scaled))
checkPars(flower.fit) # Check parameters
```

```{r}
flower.fit$pars$scaled
```

Unscaled parameters across site:
```{r}
flower.fit$pars$unscaled
```

Let's plot full data.
```{r, eval=F}
# Create plot data for prediction curves
plotdata <- metadata_usc %>% 
  group_by(site) %>% 
  summarize(mean_herb_avg = mean(herb_avg),
            min_h_apical = min(h_apical),
            max_h_apical = max(h_apical)) %>%
  add_row(site = "Bertha",
          mean_herb_avg = mean(metadata_usc$herb_avg, na.rm=T),
          min_h_apical = min(metadata_usc$h_apical, na.rm=T),
          max_h_apical = max(metadata_usc$h_apical, na.rm=T))

# Create prediction curves
N <- 100
suppressWarnings( # Hiding the follow warnings: (1) Unequal factor levels: coercing to character and (2) binding character and factor vector, coercing into character vector
  curves <- bind_rows(
    lapply(as.vector(plotdata$site), function(site) {
      i <- which(plotdata$site == site)
      data.frame(
        site = site,
        h_apical = seq(plotdata$min_h_apical[i], plotdata$max_h_apical[i], length.out = N),
        herb_avg = plotdata$mean_herb_avg[i],
        fec.flower = predict(
          flower.fit,
          type = site,
          newdata = data.frame(
            h_apical = seq(plotdata$min_h_apical[i], plotdata$max_h_apical[i], length.out = N),
            herb_avg = rep(plotdata$mean_herb_avg[i], N)
          )
        )
      )
    })
  )
)

flower.plot <- metadata_usc %>% 
  ggplot(aes(x = h_apical, 
             y = fec.flower)) + 
  geom_jitter(height = 0.1, 
              alpha = 0.3) +
  facet_wrap(~ site)

flower.plot + 
  geom_line(data = curves %>% filter(site != "Bertha")) + 
  facet_wrap(~ site)
```

# Survival

```{r}
metadata_usc <- metadata %>% filter(!is.na(h_apical),
                                    !is.na(herb_avg),
                                    fec.flower == 1, # filtering out 0s because only the sexual pathway uses the survival function
                                    !is.na(surv))

metadata_sc <- metadata_usc %>% mutate_at(.vars = vars(h_apical, herb_avg),
                                          .funs = ~ as.numeric(scale(.)))

# Get scaling parameters (really just mean and sd)
h_apical_sc <- scale(metadata_usc$h_apical)
herb_avg_sc <- scale(metadata_usc$herb_avg)
```

## Random Effects

Use nAGQ = 0 for quick approximations, but less exact form of parameter estimation.
```{r}
compute <- params$compute
savefile <- "aictabs_S_RE_Site.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 3 terms
  surv.re.site_haThe.year_haThe <- glmer(surv ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 2 terms
  surv.re.site_hePhaIhe.year_haThe <- glmer(surv ~ h_apical*herb_avg + (herb_avg + h_apical:herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_haPhaIhe.year_haThe <- glmer(surv ~ h_apical*herb_avg + (h_apical + h_apical:herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_haPhe.year_haThe <- glmer(surv ~ h_apical*herb_avg + (h_apical + herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 1 term
  surv.re.site_he.year_haThe <- glmer(surv ~ h_apical*herb_avg + (herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_ha.year_haThe <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_haIhe.year_haThe <- glmer(surv ~ h_apical*herb_avg + (h_apical:herb_avg|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 0 terms
  surv.re.site_1.year_haThe <- glmer(surv ~ h_apical*herb_avg + (1|site/transect) + (h_apical*herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  save(surv.re.site_haThe.year_haThe,
       surv.re.site_hePhaIhe.year_haThe,
       surv.re.site_haPhaIhe.year_haThe,
       surv.re.site_haPhe.year_haThe,
       surv.re.site_he.year_haThe,
       surv.re.site_ha.year_haThe,
       surv.re.site_haIhe.year_haThe,
       surv.re.site_1.year_haThe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r}
s.re.site.AIC <- aictab(list(surv.re.site_haThe.year_haThe,
            surv.re.site_hePhaIhe.year_haThe,
            surv.re.site_haPhaIhe.year_haThe,
            surv.re.site_haPhe.year_haThe,
            surv.re.site_he.year_haThe,
            surv.re.site_ha.year_haThe,
            surv.re.site_haIhe.year_haThe,
            surv.re.site_1.year_haThe),
       modnames = c("Site: height*herb", 
                    "Site: herb + height:herb", 
                    "Site: height + height:herb", 
                    "Site: height + herb",
                    "Site: herb",
                    "Site: height",
                    "Site: height:herb",
                    "Site: 1"))
s.re.site.AIC
```

Height wins.  Let's move to year:
```{r}
compute <- params$compute
savefile <- "aictabs_S_RE_Year.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 2 terms
  surv.re.site_ha.year_haPhe <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_ha.year_haPhaIhe <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_ha.year_hePhaIhe <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (herb_avg+h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 1 term
  surv.re.site_ha.year_he <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_ha.year_ha <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  surv.re.site_ha.year_haIhe <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical:herb_avg|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  # 0 terms
  surv.re.site_ha.year_1 <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (1|year), data=metadata_sc, nAGQ=0, family=binomial())
  
  save(surv.re.site_ha.year_haThe,
       surv.re.site_ha.year_hePhaIhe,
       surv.re.site_ha.year_haPhaIhe,
       surv.re.site_ha.year_haPhe,
       surv.re.site_ha.year_he,
       surv.re.site_ha.year_ha,
       surv.re.site_ha.year_haIhe,
       surv.re.site_ha.year_1, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r}
s.re.year.AIC <- aictab(list(surv.re.site_ha.year_haThe,
            surv.re.site_ha.year_hePhaIhe,
            surv.re.site_ha.year_haPhaIhe,
            surv.re.site_ha.year_haPhe,
            surv.re.site_ha.year_he,
            surv.re.site_ha.year_ha,
            surv.re.site_ha.year_haIhe,
            surv.re.site_ha.year_1),
       modnames = c("Year: height*herb", 
                    "Year: herb + height:herb", 
                    "Year: height + height:herb", 
                    "Year: height + herb",
                    "Year: herb",
                    "Year: height",
                    "Year: height:herb",
                    "Year: 1"))

s.re.year.AIC
```

```{r}
compute <- params$compute
savefile <- "aictabs_S_Sing_1.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  surv.fe.haThe.re.site_ha.year_haPhe <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical+herb_avg|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  rePCA(surv.fe.haThe.re.site_ha.year_haPhe)

  save(surv.fe.haThe.re.site_ha.year_haPhe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

We have a singularity issue.  Looks like issue is in the year random effect.  Let's drop herbivory.
```{r}
compute <- params$compute
savefile <- "aictabs_S_Sing_2.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  surv.fe.haThe.re.site_ha.year_ha <- glmer(surv ~ h_apical*herb_avg + (h_apical|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  save(surv.fe.haThe.re.site_ha.year_ha, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}

rePCA(surv.fe.haThe.re.site_ha.year_ha)
```

## Fixed Effects

```{r}
compute <- params$compute
savefile <- "aictabs_S_FE.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 2 terms
  surv.fe.haPhe.re.site_ha.year_ha <- glmer(surv ~ h_apical+herb_avg + (h_apical|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  surv.fe.haPhaIhe.re.site_ha.year_ha <- glmer(surv ~ h_apical+h_apical:herb_avg + (h_apical|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  surv.fe.hePhaIhe.re.site_ha.year_ha <- glmer(surv ~ herb_avg+h_apical:herb_avg + (h_apical|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  # 1 term
  surv.fe.ha.re.site_ha.year_ha <- glmer(surv ~ h_apical + (h_apical|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  surv.fe.he.re.site_ha.year_ha <- glmer(surv ~ herb_avg + (h_apical|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  surv.fe.haIhe.re.site_ha.year_ha <- glmer(surv ~ h_apical:herb_avg + (h_apical|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  # 0 terms
  surv.fe.1.re.site_ha.year_ha <- glmer(surv ~ 1 + (h_apical|site/transect) + (h_apical|year), data=metadata_sc, nAGQ=1, family=binomial(), control=glmerCtrl)
  
  save(surv.fe.haThe.re.site_ha.year_ha,
       surv.fe.hePhaIhe.re.site_ha.year_ha,
       surv.fe.haPhaIhe.re.site_ha.year_ha,
       surv.fe.haPhe.re.site_ha.year_ha,
       surv.fe.he.re.site_ha.year_ha,
       surv.fe.ha.re.site_ha.year_ha,
       surv.fe.haIhe.re.site_ha.year_ha,
       surv.fe.1.re.site_ha.year_ha, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r}
s.fe.AIC <- aictab(list(surv.fe.haThe.re.site_ha.year_ha,
            surv.fe.hePhaIhe.re.site_ha.year_ha,
            surv.fe.haPhaIhe.re.site_ha.year_ha,
            surv.fe.haPhe.re.site_ha.year_ha,
            surv.fe.he.re.site_ha.year_ha,
            surv.fe.ha.re.site_ha.year_ha,
            surv.fe.haIhe.re.site_ha.year_ha,
            surv.fe.1.re.site_ha.year_ha),
       modnames = c("Fixed: height*herb", 
                    "Fixed: herb + height:herb", 
                    "Fixed: height + height:herb", 
                    "Fixed: height + herb",
                    "Fixed: herb",
                    "Fixed: height",
                    "Fixed: height:herb",
                    "Fixed: 1"))

s.fe.AIC
```

Winner:
```{r}
summary(surv.fe.haPhe.re.site_ha.year_ha)
```

## Model Validation and Diagnostics

Now some diagnostics (aka model validation). Creating standard residual plots.
```{r}
par(mfrow=c(2,2))
plot(fitted(surv.fe.haPhe.re.site_ha.year_ha), residuals(surv.fe.haPhe.re.site_ha.year_ha, "deviance"), xlab="Fitted values", ylab="Deviance residuals")
plot(metadata_sc$h_apical, residuals(surv.fe.haPhe.re.site_ha.year_ha, "deviance"), xlab="Apical height", ylab="Deviance residuals")
plot(metadata_sc$herb_avg, residuals(surv.fe.haPhe.re.site_ha.year_ha, "deviance"), xlab="Herbivory average", ylab="Deviance residuals")
par(mfrow=c(1,1))
```

DHARMa Diagnostics. Same process as above. 
```{r}
surv.simulationOutput = DHARMa::simulateResiduals(fittedModel = surv.fe.haPhe.re.site_ha.year_ha, n=1000)
```

```{r}
DHARMa::plotSimulatedResiduals(surv.simulationOutput)
DHARMa::plotResiduals(metadata_sc$h_apical, surv.simulationOutput$scaledResiduals)
DHARMa::plotResiduals(metadata_sc$herb_avg, surv.simulationOutput$scaledResiduals)
```

Here we do not pass the Uniformity test, although the p-value is notably large.
```{r}
DHARMa::testUniformity(surv.simulationOutput)
```

## Model Validation and Diagnostics

Now some diagnostics (aka model validation).
```{r}
par(mfrow=c(2,2))
plot(fitted(growth.fe.haThe.site_ha.year_haPhe), residuals(growth.fe.haThe.site_ha.year_haPhe, "deviance"), xlab="Fitted values", ylab="Deviance residuals")
plot(metadata_sc$h_apical, residuals(growth.fe.haThe.site_ha.year_haPhe, "deviance"), xlab="Apical height", ylab="Deviance residuals")
plot(metadata_sc$herb_avg, residuals(growth.fe.haThe.site_ha.year_haPhe, "deviance"), xlab="Herbivory average", ylab="Deviance residuals")
par(mfrow=c(1,1))
```

DHARMa Diagnostics
```{r}
growth.simulationOutput = DHARMa::simulateResiduals(fittedModel = growth.fe.haThe.site_ha.year_haPhe, n=1000)
```

```{r}
DHARMa::plotSimulatedResiduals(growth.simulationOutput)
DHARMa::plotResiduals(metadata_sc$h_apical, growth.simulationOutput$scaledResiduals)
DHARMa::plotResiduals(metadata_sc$herb_avg, growth.simulationOutput$scaledResiduals)
```

Low p-value again may be due to large sample. Plots look ok if you exclude the tails and concentrate on where most of the data is centered, however the shape could be improved.
```{r}
DHARMa::testUniformity(growth.simulationOutput)
```

## Create AIC Tables

### Random Effect: Site

Let's format this puppy:
```{r}
ft <- flextable(s.re.site.AIC) %>%
  add_header(Modnames = "Survival: Site Random Effect") %>%
  fontsize(part = "header", size = 12) %>%
  set_header_labels(Modnames = "Model") %>% 
  bg(i = 1, bg = "#dedede") %>% 
  width(j = ~ Modnames, width = 2.6) %>%
  set_formatter(
    K = function(x) sprintf("%d", x)
  )
ft
```

Now save as image:
```{r}
# create an Rmd file ----
rmd_name <- tempfile(fileext = ".Rmd")
cat("```{r echo=FALSE}\nft\n```", file = rmd_name)
# render as an html file ----
html_name <- tempfile(fileext = ".html")
rmarkdown::render(rmd_name, output_format = "html_document", output_file = html_name)
# get a png from the html file with webshot ----
webshot(html_name, zoom = 2, file = "survivalRE_Site_AIC.png", 
        selector = "body > div.container-fluid.main-container > div.tabwid > table")
```

### Random Effect: Year

Let's format this puppy:
```{r}
ft <- flextable(s.re.year.AIC) %>%
  add_header(Modnames = "Survival: Year Random Effect") %>%
  fontsize(part = "header", size = 12) %>%
  set_header_labels(Modnames = "Model") %>% 
  bg(i = 1, bg = "#dedede") %>% 
  width(j = ~ Modnames, width = 2.6) %>%
  set_formatter(
    K = function(x) sprintf("%d", x)
  )
ft
```

Now save as image:
```{r}
# create an Rmd file ----
rmd_name <- tempfile(fileext = ".Rmd")
cat("```{r echo=FALSE}\nft\n```", file = rmd_name)
# render as an html file ----
html_name <- tempfile(fileext = ".html")
rmarkdown::render(rmd_name, output_format = "html_document", output_file = html_name)
# get a png from the html file with webshot ----
webshot(html_name, zoom = 2, file = "survivalRE_Year_AIC.png", 
        selector = "body > div.container-fluid.main-container > div.tabwid > table")
```

### Dealing with singularity

```{r}
s.singularity.AIC <- aictab(list(surv.fe.haThe.re.site_ha.year_haPhe,
                                 surv.fe.haThe.re.site_ha.year_ha),
                            modnames = c("(S) Site: h_apical, Year: h_apical+height",
                                         "(NS) Site: h_apical, Year: h_apical"))
s.singularity.AIC
```

Let's format this puppy:
```{r}
ft <- flextable(s.singularity.AIC) %>%
  add_header(Modnames = "Survival: Singularity Adjustments") %>%
  fontsize(part = "header", size = 12) %>%
  set_header_labels(Modnames = "Model") %>% 
  bg(i = 2, bg = "#dedede") %>% 
  width(j = ~ Modnames, width = 2.6) %>%
  set_formatter(
    K = function(x) sprintf("%d", x)
  )
ft
```

Now save as image:
```{r}
# create an Rmd file ----
rmd_name <- tempfile(fileext = ".Rmd")
cat("```{r echo=FALSE}\nft\n```", file = rmd_name)
# render as an html file ----
html_name <- tempfile(fileext = ".html")
rmarkdown::render(rmd_name, output_format = "html_document", output_file = html_name)
# get a png from the html file with webshot ----
webshot(html_name, zoom = 2, file = "survivalRE_Singularity_AIC.png", 
        selector = "body > div.container-fluid.main-container > div.tabwid > table")
```

### Fixed Effects

Let's format this puppy:
```{r}
ft <- flextable(s.fe.AIC) %>%
  add_header(Modnames = "Survival: Fixed Effects") %>%
  fontsize(part = "header", size = 12) %>%
  set_header_labels(Modnames = "Model") %>% 
  bg(i = 5, bg = "#dedede") %>% 
  width(j = ~ Modnames, width = 2.6) %>%
  set_formatter(
    K = function(x) sprintf("%d", x)
  )
ft
```

Now save as image:
```{r}
# create an Rmd file ----
rmd_name <- tempfile(fileext = ".Rmd")
cat("```{r echo=FALSE}\nft\n```", file = rmd_name)
# render as an html file ----
html_name <- tempfile(fileext = ".html")
rmarkdown::render(rmd_name, output_format = "html_document", output_file = html_name)
# get a png from the html file with webshot ----
webshot(html_name, zoom = 2, file = "survivalFE_AIC.png", 
        selector = "body > div.container-fluid.main-container > div.tabwid > table")
```

## Visualizations

Create model class
```{r}
# Create model class
scaled <- list(h_apical = h_apical_sc, herb_avg = herb_avg_sc)
surv.fit <- mwMod(list(mdl = surv.fe.haPhe.re.site_ha.year_ha, vars = c("h_apical", "herb_avg"), scaled = scaled))
checkPars(surv.fit) # Check parameters
```

```{r}
surv.fit$pars$scaled
```

Unscaled parameters across site:
```{r}
surv.fit$pars$unscaled
```

(Plot later)

# Growth

```{r}
# Transform data
metadata_usc <- metadata %>% filter(!is.na(h_apical),
                                    !is.na(h_apical.next),
                                    !is.na(herb_avg),
                                    fec.flower == 1, #growth is also only used in the sexual pathway
                                    surv == 1) %>%   #plants must survive until september to reprodcude in our model
  mutate(log_herb_avg = log(0.01 + herb_avg), arcsin_herb_avg = asin(sqrt(herb_avg/6)), h_apical_sq = h_apical*h_apical)
                                        
metadata_sc <- metadata_usc %>% mutate_at(.vars = vars(h_apical, h_apical.next, herb_avg, log_herb_avg, arcsin_herb_avg, h_apical_sq),
                                          .funs = funs(as.numeric(scale(.))))

# Get scaling parameters (really just mean and sd)
h_apical_sc <- scale(metadata_usc$h_apical)
h_apical.next_sc <- scale(metadata_usc$h_apical.next)
herb_avg_sc <- scale(metadata_usc$herb_avg)
log_herb_avg_sc = scale(metadata_usc$log_herb_avg)
arcsin_herb_avg_sc = scale(metadata_usc$arcsin_herb_avg)
h_apical_sq_sc = scale(metadata_usc$h_apical_sq)
```

As this is a bona-fide LME, we can do the method mentioned in Zuur.  First, model selection on random effects with REML.

## Random Effects

```{r}
growth.re.site_haThe.year_haThe <- lmer(h_apical.next~h_apical*herb_avg + (h_apical*herb_avg|site/transect)+(h_apical*herb_avg|year), data=metadata_sc, REML=T, control=lmerCtrl)
summary(growth.re.site_haThe.year_haThe)
```

First drop interaction term on site.
```{r}
growth.re.site_haPhe.year_haThe <- lmer(h_apical.next~h_apical*herb_avg + (h_apical+herb_avg|site/transect)+(h_apical*herb_avg|year),data=metadata_sc, REML=T, control=lmerCtrl)
summary(growth.re.site_haPhe.year_haThe)
```

Now drop herbivory on site.
```{r}
growth.re.site_ha.year_haThe <- lmer(h_apical.next~h_apical*herb_avg + (h_apical|site/transect)+(h_apical*herb_avg|year),data=metadata_sc, REML=T, control=lmerCtrl)
summary(growth.re.site_ha.year_haThe)
```

Now drop interaction term on year.
```{r}
growth.re.site_ha.year_haPhe <- lmer(h_apical.next~h_apical*herb_avg + (h_apical|site/transect)+(h_apical+herb_avg|year),data=metadata_sc, REML=T, control=lmerCtrl)
summary(growth.re.site_ha.year_haPhe)
```

Now drop herbivory on year.
```{r}
growth.re.site_ha.year_ha <- lmer(h_apical.next~h_apical*herb_avg + (h_apical|site/transect)+(h_apical|year),data=metadata_sc, REML=T, control=lmerCtrl)
# growth.reg.mdl4=lmer(h_apical.next~h_apical*herb_avg + (h_apical|site/transect)+(herb_avg|year),data=metadata_sc, REML=T)
summary(growth.re.site_ha.year_ha)
```

```{r}
growth.re.transect_ha.year_haPhe <- lmer(h_apical.next~h_apical*herb_avg + (h_apical|transect)+(h_apical+herb_avg|year),data=metadata_sc, REML=T, control=lmerCtrl)
```

Let's check model selection with candidates.
```{r}
growth.re.AIC <- aictab(list(growth.re.site_haThe.year_haThe,
            growth.re.site_haPhe.year_haThe,
            growth.re.site_ha.year_haThe,
            growth.re.site_ha.year_haPhe,
            growth.re.site_ha.year_ha,
            growth.re.transect_ha.year_haPhe),
       modnames = c('(S) Site: herbivory*height, Year: herbivory*height', 
                    '(S) Site: herbivory+height, Year: herbivory*height', 
                    '(S) Site: height, Year: herbivory*height', 
                    '(NS) Site: height, Year: herbivory+height', 
                    '(NS) Site: height, Year: height',
                    '(NS) Transect: height, Year: height+herbivory'))
sapply(list(growth.re.site_haThe.year_haThe,
            growth.re.site_haPhe.year_haThe,
            growth.re.site_ha.year_haThe,
            growth.re.site_ha.year_haPhe,
            growth.re.site_ha.year_ha,
            growth.re.transect_ha.year_haPhe), function(x) { isSingular(x) }, simplify = TRUE)
growth.re.AIC
```

## Fixed effects

```{r}
growth.fe.haThe.site_ha.year_haPhe <- lmer(h_apical.next ~ h_apical*herb_avg + (h_apical|site/transect)+(h_apical+herb_avg|year), data=metadata_sc, REML=F, control=lmerCtrl)

# 2 terms
growth.fe.haPhe.site_ha.year_haPhe <- lmer(h_apical.next ~ h_apical+herb_avg + (h_apical|site/transect)+(h_apical+herb_avg|year), data=metadata_sc, REML=F, control=lmerCtrl)

growth.fe.haPhaIhe.site_ha.year_haPhe <- lmer(h_apical.next ~ h_apical+h_apical:herb_avg + (h_apical|site/transect)+(h_apical+herb_avg|year), data=metadata_sc, REML=F, control=lmerCtrl)

growth.fe.hePhaIhe.site_ha.year_haPhe <- lmer(h_apical.next ~ herb_avg+h_apical:herb_avg + (h_apical|site/transect)+(h_apical+herb_avg|year), data=metadata_sc, REML=F, control=lmerCtrl)

# 1 term
growth.fe.ha.site_ha.year_haPhe <- lmer(h_apical.next ~ h_apical + (h_apical|site/transect)+(h_apical+herb_avg|year), data=metadata_sc, REML=F, control=lmerCtrl)

growth.fe.he.site_ha.year_haPhe <- lmer(h_apical.next ~ herb_avg + (h_apical|site/transect)+(h_apical+herb_avg|year), data=metadata_sc, REML=F, control=lmerCtrl)

growth.fe.haIhe.site_ha.year_haPhe <- lmer(h_apical.next ~ h_apical:herb_avg + (h_apical|site/transect)+(h_apical+herb_avg|year), data=metadata_sc, REML=F, control=lmerCtrl)

# 0 terms
growth.fe.1.site_ha.year_haPhe <- lmer(h_apical.next ~ 1 + (h_apical|site/transect)+(h_apical+herb_avg|year), data=metadata_sc, REML=F, control=lmerCtrl)
```

```{r}
growth.fe.AIC <- aictab(list(growth.fe.haThe.site_ha.year_haPhe,
                             growth.fe.haPhe.site_ha.year_haPhe,
                             growth.fe.haPhaIhe.site_ha.year_haPhe,
                             growth.fe.hePhaIhe.site_ha.year_haPhe,
                             growth.fe.ha.site_ha.year_haPhe,
                             growth.fe.he.site_ha.year_haPhe,
                             growth.fe.haIhe.site_ha.year_haPhe,
                             growth.fe.1.site_ha.year_haPhe),
                        modnames = c("Fixed: height*herb",
                                     "Fixed: height+herb",
                                     "Fixed: height+height:herb",
                                     "Fixed: herb+height:herb",
                                     "Fixed: height",
                                     "Fixed: herb",
                                     "Fixed: height:herb",
                                     "Fixed: 1"))
growth.fe.AIC
```

Winner:
```{r}
summary(growth.fe.haThe.site_ha.year_haPhe)
```
## Model Validation and Diagnostics
Now some diagnostics (aka model validation).
```{r}
par(mfrow=c(2,2))
plot(fitted(growth.fe.haThe.site_ha.year_haPhe), residuals(growth.fe.haThe.site_ha.year_haPhe, "deviance"), xlab="Fitted values", ylab="Deviance residuals")
plot(metadata_sc$h_apical, residuals(growth.fe.haThe.site_ha.year_haPhe, "deviance"), xlab="Apical height", ylab="Deviance residuals")
plot(metadata_sc$herb_avg, residuals(growth.fe.haThe.site_ha.year_haPhe, "deviance"), xlab="Herbivory average", ylab="Deviance residuals")
par(mfrow=c(1,1))
```

DHARMa Diagnostics
```{r}
growth.simulationOutput = DHARMa::simulateResiduals(fittedModel = growth.fe.haThe.site_ha.year_haPhe, n=1000)
```

```{r}
DHARMa::plotSimulatedResiduals(growth.simulationOutput)
DHARMa::plotResiduals(metadata_sc$h_apical, growth.simulationOutput$scaledResiduals)
DHARMa::plotResiduals(metadata_sc$herb_avg, growth.simulationOutput$scaledResiduals)
```

Low p-value again may be due to large sample. Plots look ok if you exclude the tails and concentrate on where most of the data is centered, however the shape could be improved.
```{r}
DHARMa::testUniformity(growth.simulationOutput)
```

### Herb_avg transform
Let's try transforming herb_avg and putting that into the existing model structure. Going with log and an arcsine transform on the herbivory average scaled to be 0<herb_avg<1. 
```{r}
growth.fe.haThe.site_ha.year_haPhe.log = lmer(h_apical.next ~ h_apical*log_herb_avg + (h_apical|site/transect)+(h_apical*log_herb_avg|year), data=metadata_sc, REML=F)
summary(growth.fe.haThe.site_ha.year_haPhe.log)
growth.fe.haThe.site_ha.year_haPhe.arcsin = lmer(h_apical.next ~ h_apical*arcsin_herb_avg + (h_apical|site/transect)+(h_apical*arcsin_herb_avg|year), data=metadata_sc, REML=F)
summary(growth.fe.haThe.site_ha.year_haPhe.arcsin)

#both transformations produce a much lower AIC, with log coming out on top
aictab(list(growth.fe.haThe.site_ha.year_haPhe, growth.fe.haThe.site_ha.year_haPhe.log, growth.fe.haThe.site_ha.year_haPhe.arcsin), modnames = c('growth.fe.haThe.site_ha.year_haPhe', 'growth.fe.haThe.site_ha.year_haPhe.log', 'growth.fe.haThe.site_ha.year_haPhe.arcsin'))
```

Both have MUCH lower AICc than the final model, so let's see what model validation says.
```{r}
par(mfrow=c(2,2))
plot(fitted(growth.fe.haThe.site_ha.year_haPhe.log), residuals(growth.fe.haThe.site_ha.year_haPhe.log, "deviance"), xlab="Fitted values", ylab="Deviance residuals")
plot(metadata_sc$h_apical, residuals(growth.fe.haThe.site_ha.year_haPhe.log, "deviance"), xlab="Apical height", ylab="Deviance residuals")
plot(metadata_sc$herb_avg, residuals(growth.fe.haThe.site_ha.year_haPhe.log, "deviance"), xlab="log(Herbivory average)", ylab="Deviance residuals")
par(mfrow=c(1,1))

par(mfrow=c(2,2))
plot(fitted(growth.fe.haThe.site_ha.year_haPhe.arcsin), residuals(growth.fe.haThe.site_ha.year_haPhe.arcsin, "deviance"), xlab="Fitted values", ylab="Deviance residuals")
plot(metadata_sc$h_apical, residuals(growth.fe.haThe.site_ha.year_haPhe.arcsin, "deviance"), xlab="Apical height", ylab="Deviance residuals")
plot(metadata_sc$herb_avg, residuals(growth.fe.haThe.site_ha.year_haPhe.arcsin, "deviance"), xlab="arcsin(sqrt(Herbivory average))", ylab="Deviance residuals")
par(mfrow=c(1,1))
```
None of these residual plots look any better, so we will see what DHARMa says.
```{r}
growth.simulationOutput.log = DHARMa::simulateResiduals(fittedModel = growth.fe.haThe.site_ha.year_haPhe.log, n=1000)
growth.simulationOutput.arcsin = DHARMa::simulateResiduals(fittedModel = growth.fe.haThe.site_ha.year_haPhe.arcsin, n=1000)
```

```{r}
DHARMa::plotSimulatedResiduals(growth.simulationOutput.log)
DHARMa::plotResiduals(metadata_sc$h_apical, growth.simulationOutput.log$scaledResiduals)
DHARMa::plotResiduals(metadata_sc$log_herb_avg, growth.simulationOutput.log$scaledResiduals)

DHARMa::plotSimulatedResiduals(growth.simulationOutput.arcsin)
DHARMa::plotResiduals(metadata_sc$h_apical, growth.simulationOutput.arcsin$scaledResiduals)
DHARMa::plotResiduals(metadata_sc$arcsin_herb_avg, growth.simulationOutput.arcsin$scaledResiduals)

DHARMa::testUniformity(growth.simulationOutput.log)
DHARMa::testUniformity(growth.simulationOutput.arcsin)
```

```{r}
# Create model class
scaled <- list(h_apical = h_apical_sc, herb_avg = herb_avg_sc, h_apical.next = h_apical.next_sc)
growth.fit <- mwMod(list(mdl = growth.fe.haThe.site_ha.year_haPhe, vars = c("h_apical", "herb_avg", "h_apical.next"), scaled = scaled))
checkPars(growth.fit) # Check parameters
```

# Pods

```{r}
metadata_usc <- metadata %>% filter(!is.na(h_apical),
                                    !is.na(h_apical.next),
                                    !is.na(herb_avg),
                                    fec.flower == 1, #pods only result from the sexual pathway
                                    surv == 1, #again, plants must survive to September
                                    !is.na(N_pods),
                                    h_apical.next > 50,
                                    !(site == "YTB" & h_apical <= 50)) #necessary to compensate for an issue with some of the plants in YTB site

metadata_sc <- metadata_usc %>% mutate_at(.vars = vars(h_apical, h_apical.next, herb_avg),
                                          .funs = ~ as.numeric(scale(.)))

# Get scaling parameters (really just mean and sd)
h_apical_sc <- scale(metadata_usc$h_apical)
h_apical.next_sc <- scale(metadata_usc$h_apical.next)
herb_avg_sc <- scale(metadata_usc$herb_avg)
```

### June vs. September Height as a Predictor
First, do full model. In this case, we will compare to see if height in June or September is a better predictor.
```{r}
pods.reg.full_sept = glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next*herb_avg|site/transect)+(h_apical.next*herb_avg|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control=glmerCtrl)

pods.reg.full_june = glmer(N_pods ~ h_apical*herb_avg + (h_apical*herb_avg|site/transect)+(h_apical*herb_avg|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control=glmerCtrl)

aictab(list(pods.reg.full_june, pods.reg.full_sept), modnames = c('June', 'September'))
summary(pods.reg.full_sept)
```

### Random Effects
September wins, so we will continue to use this in our model instead of height in June (h_apical). Now onto selection for random effects. We can try and drop the herb_avg term in the site/transect random effect first due to small variation.

Use nAGQ = 0 for quick approximations, but less exact form of parameter estimation.
```{r}
compute <- params$compute
savefile <- "aictabs_P_RE_Site.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 3 terms
  pods.re.site_haThe.year_haThe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next*herb_avg|site/transect) + (h_apical.next*herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  # 2 terms
  pods.re.site_hePhaIhe.year_haThe <- glmer(N_pods ~ h_apical.next*herb_avg + (herb_avg + h_apical.next:herb_avg|site/transect) + (h_apical.next*herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_haPhaIhe.year_haThe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next + h_apical.next:herb_avg|site/transect) + (h_apical.next*herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_haPhe.year_haThe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next + herb_avg|site/transect) + (h_apical.next*herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  # 1 term
  pods.re.site_he.year_haThe <- glmer(N_pods ~ h_apical.next*herb_avg + (herb_avg|site/transect) + (h_apical.next*herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_ha.year_haThe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next|site/transect) + (h_apical.next*herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_haIhe.year_haThe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next:herb_avg|site/transect) + (h_apical.next*herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  # 0 terms
  pods.re.site_1.year_haThe <- glmer(N_pods ~ h_apical.next*herb_avg + (1|site/transect) + (h_apical.next*herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  save(pods.re.site_haThe.year_haThe,
       pods.re.site_hePhaIhe.year_haThe,
       pods.re.site_haPhaIhe.year_haThe,
       pods.re.site_haPhe.year_haThe,
       pods.re.site_he.year_haThe,
       pods.re.site_ha.year_haThe,
       pods.re.site_haIhe.year_haThe,
       pods.re.site_1.year_haThe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r}
pods.re.site.AIC <- aictab(list(pods.re.site_haThe.year_haThe,
            pods.re.site_hePhaIhe.year_haThe,
            pods.re.site_haPhaIhe.year_haThe,
            pods.re.site_haPhe.year_haThe,
            pods.re.site_he.year_haThe,
            pods.re.site_ha.year_haThe,
            pods.re.site_haIhe.year_haThe,
            pods.re.site_1.year_haThe),
       modnames = c("Site: height*herb", 
                    "Site: herb + height:herb", 
                    "Site: height + height:herb", 
                    "Site: height + herb",
                    "Site: herb",
                    "Site: height",
                    "Site: height:herb",
                    "Site: 1"))
pods.re.site.AIC
```

Height on site wins.  Let's move on the year.
```{r}
compute <- params$compute
savefile <- "aictabs_P_RE_Year.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 2 terms
  pods.re.site_ha.year_haPhe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next|site/transect) + (h_apical.next+herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_ha.year_haPhaIhe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next|site/transect) + (h_apical.next+h_apical.next:herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_ha.year_hePhaIhe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next|site/transect) + (herb_avg+h_apical.next:herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  # 1 term
  pods.re.site_ha.year_he <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next|site/transect) + (herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_ha.year_ha <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next|site/transect) + (h_apical.next|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  pods.re.site_ha.year_haIhe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next|site/transect) + (h_apical.next:herb_avg|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  # 0 terms
  pods.re.site_ha.year_1 <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next|site/transect) + (1|year), data=metadata_sc, nAGQ=0, family=poisson(link='log'))
  
  save(pods.re.site_ha.year_haThe,
       pods.re.site_ha.year_hePhaIhe,
       pods.re.site_ha.year_haPhaIhe,
       pods.re.site_ha.year_haPhe,
       pods.re.site_ha.year_he,
       pods.re.site_ha.year_ha,
       pods.re.site_ha.year_haIhe,
       pods.re.site_ha.year_1, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r}
p.re.year.AIC <- aictab(list(pods.re.site_haPhe.year_haThe,
            pods.re.site_ha.year_hePhaIhe,
            pods.re.site_ha.year_haPhaIhe,
            pods.re.site_ha.year_haPhe,
            pods.re.site_ha.year_he,
            pods.re.site_ha.year_ha,
            pods.re.site_ha.year_haIhe,
            pods.re.site_ha.year_1),
       modnames = c("Year: height*herb", 
                    "Year: herb + height:herb", 
                    "Year: height + height:herb", 
                    "Year: height + herb",
                    "Year: herb",
                    "Year: height",
                    "Year: height:herb",
                    "Year: 1"))

p.re.year.AIC
```

Herbivory + height:herb wins.  Let's check singularity:
```{r}
compute <- params$compute
savefile <- "aictabs_P_Sing_1.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  pods.fe.haThe.re.site_ha.year_hePhaIhe <- glmer(N_pods ~ h_apical.next*herb_avg + (h_apical.next|site/transect) + (herb_avg+h_apical.next:herb_avg|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'))
  
  save(pods.fe.haThe.re.site_ha.year_hePhaIhe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
rePCA(pods.fe.haThe.re.site_ha.year_hePhaIhe)
```

Because the model failed to converge, it looks singular. Let's try dropping the variable in site.

```{r}
compute <- params$compute
savefile <- "aictabs_P_Sing_2.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  pods.fe.haThe.re.site_1.year_hePhaIhe <- glmer(N_pods ~ h_apical.next*herb_avg + (1|site/transect) + (herb_avg+h_apical.next:herb_avg|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'))
  
  save(pods.fe.haThe.re.site_1.year_hePhaIhe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
rePCA(pods.fe.haThe.re.site_1.year_hePhaIhe)
```

This fixed the singularity in our model!

## Fixed effects

```{r}
compute <- params$compute
savefile <- "aictabs_P_FE.RData"

if (!file.exists(file.path(mwCache,savefile)) || (compute)) {
  # 2 terms
  pods.fe.haPhe.re.site_1.year_hePhaIhe <- glmer(N_pods ~ h_apical.next+herb_avg + (1|site/transect) + (herb_avg+h_apical.next|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control=glmerCtrl)
  
  pods.fe.haPhaIhe.re.site_1.year_hePhaIhe <- glmer(N_pods ~ h_apical.next+h_apical.next:herb_avg + (1|site/transect) + (herb_avg+h_apical.next|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control=glmerCtrl)
  
  pods.fe.hePhaIhe.re.site_1.year_hePhaIhe <- glmer(N_pods ~ herb_avg+h_apical.next:herb_avg + (1|site/transect) + (herb_avg+h_apical.next|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control=glmerCtrl)
  
  # 1 term
  pods.fe.ha.re.site_1.year_hePhaIhe <- glmer(N_pods ~ h_apical.next + (1|site/transect) + (herb_avg+h_apical.next|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control=glmerCtrl)
  
  pods.fe.he.re.site_1.year_hePhaIhe <- glmer(N_pods ~ herb_avg + (1|site/transect) + (herb_avg+h_apical.next|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control=glmerCtrl)
  
  pods.fe.haIhe.re.site_1.year_hePhaIhe <- glmer(N_pods ~ h_apical.next:herb_avg + (1|site/transect) + (herb_avg+h_apical.next|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control=glmerCtrl)
  
  # 0 terms
  pods.fe.1.re.site_1.year_hePhaIhe <- glmer(N_pods ~ 1 + (1|site/transect) + (herb_avg+h_apical.next|year), data=metadata_sc, nAGQ=1, family=poisson(link='log'), control=glmerCtrl)
  
  save(pods.fe.haThe.re.site_1.year_hePhaIhe,
       pods.fe.hePhaIhe.re.site_1.year_hePhaIhe,
       pods.fe.haPhaIhe.re.site_1.year_hePhaIhe,
       pods.fe.haPhe.re.site_1.year_hePhaIhe,
       pods.fe.he.re.site_1.year_hePhaIhe,
       pods.fe.ha.re.site_1.year_hePhaIhe,
       pods.fe.haIhe.re.site_1.year_hePhaIhe,
       pods.fe.1.re.site_1.year_hePhaIhe, 
       file=file.path(mwCache,savefile))
} else {
  load(file.path(mwCache,savefile))
}
```

```{r}
p.fe.AIC <- aictab(list(pods.fe.haThe.re.site_1.year_hePhaIhe,
            pods.fe.hePhaIhe.re.site_1.year_hePhaIhe,
            pods.fe.haPhaIhe.re.site_1.year_hePhaIhe,
            pods.fe.haPhe.re.site_1.year_hePhaIhe,
            pods.fe.he.re.site_1.year_hePhaIhe,
            pods.fe.ha.re.site_1.year_hePhaIhe,
            pods.fe.haIhe.re.site_1.year_hePhaIhe,
            pods.fe.1.re.site_1.year_hePhaIhe),
       modnames = c("Fixed: height*herb", 
                    "Fixed: herb + height:herb", 
                    "Fixed: height + height:herb", 
                    "Fixed: height + herb",
                    "Fixed: herb",
                    "Fixed: height",
                    "Fixed: height:herb",
                    "Fixed: 1"))
p.fe.AIC
```

Winner:
```{r}
summary(pods.fe.haThe.re.site_1.year_hePhaIhe)
```

## Model Validation and Diagnostics
```{r}
par(mfrow=c(2,2))
plot(fitted(pods.fe.haThe.re.site_1.year_hePhaIhe), residuals(pods.fe.haThe.re.site_1.year_hePhaIhe, "deviance"), xlab="Fitted values", ylab="Deviance residuals")
plot(metadata_sc$h_apical, residuals(pods.fe.haThe.re.site_1.year_hePhaIhe, "deviance"), xlab="Apical height", ylab="Deviance residuals")
plot(metadata_sc$herb_avg, residuals(pods.fe.haThe.re.site_1.year_hePhaIhe, "deviance"), xlab="Herbivory average", ylab="Deviance residuals")
par(mfrow=c(1,1))
```

DHARMa Diagnostics
```{r}
pods.simulationOutput = DHARMa::simulateResiduals(fittedModel = pods.fe.haThe.re.site_1.year_hePhaIhe, n=1000)
```

```{r}
DHARMa::plotSimulatedResiduals(pods.simulationOutput)
DHARMa::plotResiduals(metadata_sc$h_apical, pods.simulationOutput$scaledResiduals)
DHARMa::plotResiduals(metadata_sc$herb_avg, pods.simulationOutput$scaledResiduals)
```
