---
title: "Figure 5: Population growth versus herbivory"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
---

# Initialization

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(milkweed)
library(dplyr)
library(ggplot2)
requirePackages("doParallel")
library(doParallel) # Normally, I don't load suggested packages, but this one requires and loads parallel, foreach, and iterators,
                    #   so, you know, it's easier this way.
'%<>%' <- magrittr::'%<>%'
ipm <- mwIPM()
mwCache <- getOption("milkweed.cache")
```

# Get curves

```{r}
sites <- c("Bertha", "BLD1", "BLD2", "PWR", "SKY", "YTB")
minind <- max(which(ipm$vars$herb_avg$x < 0.1))
maxind <- max(which(ipm$vars$herb_avg$x < 2.0))+1
plotdata <- data.frame(herb_avg = ipm$vars$herb_avg$x[minind:maxind],
                       growth_rate = sapply(minind:maxind, 
                                            function (x) { 
                                              ipm %>% 
                                                setHerbivoryMatrix(dist.herb = c(rep(0,x-1), 1/ipm$vars$herb_avg$dx, rep(0,ipm$N-x))) %>% 
                                                analyzeGrowthRate()
                                            }),
                       disttype = "pointmass")

# Get line relating mean and sd
sitedata <- bind_cols(tbl_df(t(sapply(ipm$pars$munched.fit[2:6], function (x) {c(x$fit$estimate)}))),
                      tbl_df(data.frame(pmunch = sapply(ipm$pars$munched.fit[2:6], function (x) {c(x$pmunch)}))),
                      tbl_df(data.frame(site = sites[2:6])))
myline <- lm(sdlog ~ meanlog, data = sitedata)

munched <- ipm$pars$munched.fit[["Bertha"]]$predict
b <- ipm$vars$herb_avg$b
lx <- ipm$vars$herb_avg$x
dx <- ipm$vars$herb_avg$dx
pmunch <- ipm$pars$munched.fit[["Bertha"]]$pmunch
pmunchFit <- lm(pmunch ~ meanlog, data = sitedata)
myfunc <- function(x, mu) {
  pmunch <- predict(pmunchFit, data.frame(meanlog = x))
  y <- munched(b,
               pars = c(pmunch,
                        x,
                        predict(myline,
                                data.frame(meanlog = x))))
  return(sum(y*lx)*dx - mu)
}

plotdata <- bind_rows(plotdata,
                      data.frame(herb_avg = ipm$vars$herb_avg$x[minind:maxind],
                                 growth_rate = sapply(ipm$vars$herb_avg$x[minind:maxind],
                                                      function (x) {
                                                        meanlog <- uniroot(myfunc, c(log(0.001), log(6.001)), mu = x)$root
                                                        pmunch <- predict(pmunchFit, data.frame(meanlog = meanlog))
                                                        ipm %>%
                                                          setHerbivoryMatrix(dist.herb = munched(b,
                                                                                                 pars = c(pmunch,
                                                                                                          meanlog,
                                                                                                          predict(myline,
                                                                                                                  data.frame(meanlog = meanlog))))) %>%
                                                          analyzeGrowthRate()
                                                      }),
                                 disttype = "lnorm")
)
```

# Bootstrap data with individual clonal herbivory
Bootstrap the data to get 95% confidence ellipses for average herbivory and lambda over each site.
```{r}
compute <- FALSE
parallel <- TRUE

if (!file.exists(file.path(mwCache,"figure5a.RData")) | (compute)) {
  coreProcess <- function(ipm, sites) {
    ipm %<>% bootIPM()
    thisone <- ipm$data %>% 
      group_by(site) %>% 
      summarize(herb_avg = mean(herb_avg, na.rm=T), 
                growth_rate = NA,
                disttype = "lnorm")
    thisone$growth_rate <- sapply(sites[-1], function (x) {ipm %>% setSite(x) %>% analyzeGrowthRate()})
    return(thisone)
  }
  
  if (parallel) {
    numcl <- detectCores()-1
    registerDoParallel(cores = numcl)
    results <- tbl_df(foreach(i=1:20, .combine=bind_rows) %dopar% {
      library(milkweed)
      library(dplyr)
      library(ggplot2)
      coreProcess(ipm, sites)
    })
  } else {
    results <- do.call(rbind, lapply(1:20, function (x) {coreProcess(ipm, sites)}))
  }
  
  save(plotdata, results, file=file.path(mwCache,"figure5a.RData"))
} else {
  load(file.path(mwCache,"figure5a.RData"))
}
```

# Bootstrap data with per-capita herbivory
Bootstrap the data to get 95% confidence ellipses for average herbivory and lambda over each site.
```{r, eval=F}
compute <- FALSE
parallel <- TRUE

if (!file.exists(mwROOT("data","calculated","figure5b.RData")) | (compute)) {
  ipm <- mwIPM(list(mdlargs = list(method = "exp", input = "meanonly")))
  coreProcess <- function(ipm, sites) {
    ipm %<>% bootIPM()
    thisone <- ipm$data %>% 
      group_by(site) %>% 
      summarize(log_herb_avg = mean(log_herb_avg, na.rm=T), 
                growth_rate = NA,
                disttype = "lnorm")
    thisone$growth_rate <- sapply(sites[-1], function (x) {ipm %>% setSite(x) %>% analyzeGrowthRate()})
    return(thisone)
  }
  
  if (parallel) {
    numcl <- detectCores()-1
    registerDoParallel(cores = numcl)
    results <- tbl_df(foreach(i=1:20, .combine=bind_rows) %dopar% {
      library(milkweed)
      library(dplyr)
      library(ggplot2)
      coreProcess(ipm, sites)
    })
  } else {
    results <- do.call(rbind, lapply(1:20, function (x) {coreProcess(ipm, sites)}))
  }
  
  save(plotdata, results, file=mwROOT("data","calculated","figure5b.RData"))
} else {
  load(mwROOT("data","calculated","figure5b.RData"))
}
```

# Plotting with both curves

Render and plot the figure.
```{r}
# Bertha growth rate vs point-mass herbivory scores
p <- plotdata %>% ggplot(aes(x = herb_avg,
                             y = growth_rate,
                             linetype = disttype)) +
                  geom_line() + 
                  geom_hline(aes(yintercept = 1.0), 
                             linetype = 3)

# Site-specific bootstrapped data points with 95% confidence ellipse
p <- p + geom_point(aes(x = herb_avg, 
                        y = growth_rate, 
                        color = site,
                        linetype = NA), 
                    size = 0.5,
                    data=results) + 
         stat_ellipse(aes(x = herb_avg, 
                          y = growth_rate, 
                          color = site,
                          linetype = NA), 
                      data = results)

# Change theme, scale, and labels
p <- p + theme_bw() +
         scale_x_continuous(limits = c(0.0, 2.0)) + 
         scale_y_continuous(limits = c(0.0, 1.7)) + 
         xlab("Herbivory severity") +
         ylab(expression(paste("Population growth rate(", lambda, ")"))) + 
         labs(color = "Sites") + 
         theme(legend.background = element_rect(fill="lightgrey",
                                                size=0.1,
                                                linetype="solid"),
               legend.key.size = unit(0.18, "in"),
               legend.position = c(0.885, 0.78))

p
```

# Plot with only individual clonal herbivory

```{r}
plotdata %>% filter(disttype == "lnorm") -> plotdata2

# Bertha growth rate vs point-mass herbivory scores
p <- plotdata2 %>% ggplot(aes(x = herb_avg,
                             y = growth_rate)) +
                  geom_line() + 
                  geom_hline(aes(yintercept = 1.0), 
                             linetype = 3)

# Site-specific bootstrapped data points with 95% confidence ellipse
p <- p + geom_point(aes(x = herb_avg, 
                        y = growth_rate, 
                        color = site), 
                    size = 0.5,
                    data=results) + 
         stat_ellipse(aes(x = herb_avg, 
                          y = growth_rate, 
                          color = site), 
                      data = results)

# Change theme, scale, and labels
p <- p + theme_bw() +
         scale_x_continuous(limits = c(0.0, 1.5)) + 
         scale_y_continuous(limits = c(0.5, 1.7)) + 
         xlab("Herbivory severity") +
         ylab(expression(paste("Population growth rate (", lambda, ")"))) + 
         labs(color = "Sites") + 
         theme(legend.background = element_rect(fill="lightgrey",
                                                size=0.1,
                                                linetype="solid"),
               legend.key.size = unit(0.18, "in"),
               legend.position = c(0.885, 0.78))

p
```

Save figure.
```{r}
ggsave("Figure5_PopGrowthVsHerb.png", height=4, width=6, device = "png", p)
```
